---
title: "R Notebook"
output: html_notebook
---


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(writexl)
library(stringr)
library(lubridate)
library(rlang)

library(MAGIS100PM)
```

library(reticulate)
Sys.setenv(RETICULATE_PYTHON = "/Users/jimk/AppData/Local/Microsoft/WindowsApps/PythonSoftwareFoundation.Python.3.11_qbz5n2kfra8p0")
use_python("/Users/jimk/AppData/Local/Microsoft/WindowsApps/PythonSoftwareFoundation.Python.3.11_qbz5n2kfra8p0", required=TRUE)

#```{python}
#print("the")
#python.exe xer_extractor.py -x current
#python.exe reader.py -d -x current -S
#```


```{r}
all <- get.all.schedule("working")
charges <- get.all.kronos()
people <- get.p6.people(charges, all)
tasks.people <- combine.tasks.people(people, all)
```

```{r}
labor <- bin.labor(tasks.people)
```


```{r}
fte<- FTE.plots(labor$by.day.all%>%filter(code!='other'))
activities<- activities.plot(all$all.data, interval(as.Date('2023-09-01'),as.Date('2023-12-01')),tcost=1)
milestones<- milestones.plot(all$all.data)
resources<- resources.plot(labor$by.week, device="png")
proc<- procurements.plot(all)
```

```{r}
ggsave(resources, filename=paste(base.path,"/hours.png",sep=''), width=24, units='in', device='png')
ggsave(milestones, filename=paste(base.path,'/milestones.png',sep=''), width=12, units='in', device="png")
ggsave(activities, filename=paste(base.path,"/active.pdf",sep=''),units="in", height=12, width=24, device="pdf")
ggsave(fte[[1]], filename=paste(base.path,"/fte_role.png",sep=''),units="in", device="png")
ggsave(fte[[2]], filename=paste(base.path,"/fte_div.png",sep=''),units="in", device="png")

```


```{r}
print(proc$plot)
print(milestones)
print(fte[[1]])
print(fte[[2]])
print(fte[[3]])
print(fte[[4]])
print(resources)
```

```{r}
activities<- activities.plot(all$all.data, interval(as.Date('2024-09-01'),as.Date('2025-11-01')),tcost=1)
```

```{r}
#labor <- bin.labor(tasks.people)

persons.FY23Q34<- labor$by.week.person %>%
  filter(FY==2023)%>%
  filter(week %within% interval('2023-07-01','2023-10-01')) %>%
  group_by(person,FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805/4)) %>%
  filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, div=DSC),join_by(person) )

persons.FY23<- labor$by.week.person %>%
  filter(FY==2023) %>%
  group_by(person,FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805*FY.table['frac'][1,])) %>%
  filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name),join_by(person) )

tmp.persons<- labor$by.week.person %>%
  filter(FY==2023)

persons.FY24<- labor$by.week.person %>%
  filter(FY==2024) %>%
  group_by(person,FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name),join_by(person) )

types.FY24<- labor$by.week.all %>%
  filter(FY==2024) %>%
  group_by(type,person, FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  #filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person) )

tpt.FY<- labor$by.week.person.task %>%
  filter(FY>2022) %>%
  group_by(type,person,task_id, FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  #filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person)) %>%
  left_join(all$tasks%>%select(task_id, task_name, task_code, target_start_date, target_end_date), by=join_by(task_id))



```

This block below is all special code that really only needs to be run once or for testing.

```{r}
#all$all.data %>% 
#  mutate(yr=fiscal.from.date(target_start), days_float=total_float/8) %>%
#  filter(yr>2023) %>%
#  select(code, name, target_start, target_end, total_float, total_cost,yr, days_float) %>%
#  arrange(target_start) %>%
#  view()

# prime the rolesmap here (only needed once, then hand edited)
#rolesmap<-rbind(
#  data.frame(role=unique(charges$Function.Role))%>%mutate(type='kr'),
#  data.frame(role=unique(labor$by.week.person$type))%>%mutate(type='p6')
#)
#write_xlsx(rolesmap,"../rolesmap.xlsx")

#ctcmap<- read.csv("../ctcmap.csv",colClasses=c("character","character","character"), strip.white=TRUE)
#save(ctcmap, file="../MAGIS100PM/data/ctcmap.rda",version=2)

#rolesmap<- read_xlsx("../rolesmap.xlsx")
#save(rolesmap, file="../MAGIS100PM/data/rolesmap.rda",version=2)

#roles<- read.csv("../roles.csv", strip.white=TRUE)
#save(roles, file="../MAGIS100PM/data/roles.rda",version=2)


```

Full.Name = Full.Name
Full.Name = Role

```{r}

kr.proc <- function(grouping.name, charges)
{
  grouping.sym = rlang::sym(grouping.name)

  kr.tmp<- charges %>% filter(Timecard.Start>as.Date("2023-03-01")) %>%
    select(FY=fiscal.year, d=Timecard.Start, Hours=Hours, Full.Name=Full.Name,ctc=taskcode,department=DSC, role=Role) %>%
    mutate(LOE=ctc=='Q1903.01') %>%
    mutate(role.new=if_else(LOE=='TRUE'&!is.na(ctc), "LOE", role))

  kr.tmp.1<- kr.tmp%>% group_by(ctc, !!grouping.sym, d) %>% summarise(sum=sum(Hours),.groups='keep')
  kr.tmp.2<- kr.tmp.1%>% arrange(ctc, !!grouping.sym, d) %>% group_by(ctc, !!grouping.sym) %>% mutate(csum=cumsum(sum))
  kr.tmp.1<- rename(kr.tmp.1, grouping=grouping.name)
  kr.tmp.2<- rename(kr.tmp.2, grouping=grouping.name)

  kr.tmp.g1<- ggplot(kr.tmp.1,aes(x=d, y=sum)) + geom_step() + facet_wrap(vars(ctc,grouping),scales="free_y")
  kr.tmp.g2<- ggplot(kr.tmp.2,aes(x=d, y=csum)) + geom_step() + facet_wrap(vars(ctc,grouping),scales="free_y")

  list(kr=kr.tmp, kr1=kr.tmp.1, kr2=kr.tmp.2, kr.g1=kr.tmp.g1, kr.g2=kr.tmp.g2)
}

p6.proc <- function(grouping.name, labor.by.week)
{
  grouping.sym = rlang::sym(grouping.name)
  
  p6.tmp<- labor.by.week %>% filter(week>=as.Date("2023-03-01")&week<=as.Date("2023-09-30")) %>%
    select(FY=FY, d=week, Hours=dl.hours, Full.Name=person, department=code, ctc=ctc, role=Role) %>%
    mutate(LOE=ctc=='Q1903.01')%>%
    mutate(role.new=if_else(LOE=='TRUE'&role!="RA", "LOE", role))

  p6.tmp.1<- p6.tmp %>% group_by(ctc, !!grouping.sym, d) %>% summarise(sum=sum(Hours),.groups='keep')
  p6.tmp.2<- p6.tmp.1%>% arrange(ctc, !!grouping.sym, d) %>% group_by(ctc, !!grouping.sym) %>% mutate(csum=cumsum(sum))
  p6.tmp.1<- rename(p6.tmp.1, grouping=grouping.name)
  p6.tmp.2<- rename(p6.tmp.2, grouping=grouping.name)

  p6.tmp.g1<- ggplot(p6.tmp.1,aes(x=d, y=sum)) + geom_step() + facet_wrap(vars(ctc,grouping),scales="free_y")
  p6.tmp.g2<- ggplot(p6.tmp.2,aes(x=d, y=csum)) + geom_step() + facet_wrap(vars(ctc,grouping),scales="free_y")
  
  list(p6=p6.tmp, p61=p6.tmp.1, p62=p6.tmp.2, p6.g1=p6.tmp.g1, p6.g2=p6.tmp.g2)
}

```

Full.Name = person
Full.Name = Role

labor$by.week.person
labor$by.week.role


```{r}

#kr.data <- kr.proc("role.new", charges%>%filter(taskname=="Q1903.10"))
kr.data <- kr.proc("role.new", charges)
p6.data <- p6.proc("role.new", labor$by.week.role)
```


```{r}
print(kr.data$kr.g1)
print(kr.data$kr.g2)

ggsave(kr.data$kr.g1, filename=paste(base.path,"/HoursByName.pdf",sep=''),units="in", height=12, width=24, device="pdf")
ggsave(kr.data$kr.g2, filename=paste(base.path,"/CumuHoursByName.pdf",sep=''),units="in", height=12, width=24, device="pdf")
```

```{r}
print(p6.data$p6.g1)
print(p6.data$p6.g2)

ggsave(p6.data$p6.g1, filename=paste(base.path,"/P6HoursByName.pdf",sep=''),units="in", height=12, width=24, device="pdf")
ggsave(p6.data$p6.g2, filename=paste(base.path,"/P6CumuHoursByName.pdf",sep=''),units="in", height=12, width=24, device="pdf")

```

```{r}
#person.diff <- setdiff(unique(charges$Full.Name), unique(labor$by.week.person$person))
person.comp <- rbind(mutate(p6.data$p62,from="P6"),mutate(kr.data$kr2,from="KR"))
  #left_join(mutate(tmp.2,from="KR"), by=join_by(Full.Name,d), suffix=c(".p6",".kr"))

person.g3<- ggplot(person.comp,aes(x=d, colour=from)) + 
  geom_step(aes(y=csum)) +
  geom_step(aes(y=csum)) +
  facet_wrap(vars(ctc,grouping),scales="free_y")

print(person.g3)
ggsave(person.g3, filename=paste(base.path,"/CumuHoursByRole.pdf",sep=''),units="in", height=12, width=24, device="pdf")

tmp<- person.comp %>% ungroup() %>% select(from, d, isum=sum) %>% group_by(from,d)%>% summarise(sum=sum(isum)) %>% arrange(from, d) %>% group_by(from) %>% mutate(csum=cumsum(sum))

person.g4<- ggplot(tmp,aes(x=d, colour=from)) + 
  geom_step(aes(y=csum))# +
#  geom_step(aes(y=csum)) +
#  facet_wrap(vars(from),scales="free_y")
print(person.g4)

```
```{r}
activities<- activities.plot(all$all.data, interval(as.Date('2023-03-01'),as.Date('2023-12-31')),tcost=1)
test.gp<-ggplot(
  activities$data%>%filter(state!="Future"),
    aes( colour=as.factor(state), y=reorder(code,target_start))
  ) +
    geom_linerange(aes(xmin = early_start, xmax = early_end),colour='red',position=position_nudge(y=0.0)) +
    geom_linerange(aes(xmin = late_start, xmax = late_end), colour='green',position=position_nudge(y=0.0)) +
    geom_linerange(aes(xmin = target_start, xmax = target_end), colour='blue', linewidth=.50) +
    geom_text(aes(hjust='left',x = target_start, label = paste(total_cost,name,sep=":")), nudge_x=9.6, nudge_y=.4, size=2.0) +
    geom_text(aes(hjust='left',x = late_end, label = paste(free_float, total_float, sep='/')), nudge_x=9.6, nudge_y=.4, size=1.8) +
    scale_x_date(date_breaks='1 month', date_labels = "%b %y") +
    theme(axis.text.x = element_text(angle = 90),axis.text=element_text()) +
    labs(x="Target Start Date", y="Activity", fill="role")

  ggsave(test.gp, filename="activities.pdf",units="in", height=10, width=24, device="pdf")

  print(test.gp)
```

