---
title: "MAGIS-100 Confidence Level"
format: 
  pdf:
    df-print: kable
editor: visual
---

## 

```{r message=FALSE, warning=FALSE}
#| echo: false
library(mc2d)
library(tidyverse)

options(digits = 2)
```

# Introduction

P6 provides us with a total uncertainty that is a combination of all estimate uncertainties entered into the BOEs. From this number the system calculates a contingency value for the time period of interest (summarized yearly) at a 90% confidence level. $$P(X \le contingency) = confidence.level$$ where $x$ has a distribution calculated using all the BOE uncertainties.

Our goal here is to calculate a confidence level given what we know from P6 assuming that there is a difference amount of contingency given to the project.

Project Management resources show that many times three point estimates are used for entering estimate uncertainties. The PERT distribution\footnote{https://en.wikipedia.org/wiki/PERT\_distribution} appears to be a common distribution to use as a model for these three-point estimates in place of the a triangular distribution. The PERT distribution requires a minimum (most optimistic cost), a mode (expected cost), and a maximum (the most pessimistic cost).

![PERT distribution compared with triangular \footnote{https://project-management.info/wp-content/uploads/2020/01/PERT-Triangular-Probability-Density-Curve-1024x540.jpg}](C:/Users/jimk/OneDrive%20-%20Fermi%20National%20Accelerator%20Laboratory/Documents/MAGIS-100/read_stuff/pert-dist-crop.pdf){width="70%"}

If we assume very minimal information about the distribution that drives the calculation of the total uncertainty, we can make a crude estimate of confidence level for any given contingency number using the PERT distribution. Assuming $X \sim PERT(min, mode, max)$ with $min=-max$ and $mode=0$, for each fiscal year $f$, find $max_f$ such that $P_{max_f}(X_{f} \le x_{f}) = CL$ for $CL=.90$ and $x_f$ the contingencies from the P6 generated budget table. Use these $max_f$ values to calculate $CL_f$ for differences of yearly planned work and funding guidance values as contingency $x_f$ (or as we have been calling it, reserve)\footnote{This notation is sloppy}.

# Estimating the confidence level given some contingency value

Find the contingency value given the PERT maximum bound and desired confidence level $P(X \le value; bound)=CL$. The bounds are assumed symmetrical here. We will also test with the triangular distribution.

```{r}
func.q <- function(quant) { function(bound, prob) { quant(c(prob),-bound, 0, bound) } }
calc.qpert <- func.q(qpert)
calc.qtriang <- func.q(qtriang)

```

Find the confidence level $P(X \le contin; bound) = CL$, given a contingency value and PERT maximum bound.

```{r}
func.p <- function(distr) { function(contin, bound) { distr(c(contin),-bound, 0, bound) } }
calc.ppert <- func.p(ppert)
calc.ptriang <- func.p(ptriang)
```

We want to find the PERT maximum bound that yields a confidence level $cl$ and contingency of $contin$. This function calculates a simple distance from a desired contingency $contin$ and $cl$ given a high bound of the quantile function $calc$. This returned function can be used as function for the optimizer to minimize.

```{r}
optfunc<- function(cl, contin,calc) { function (maxbound) {(calc(maxbound,cl)-contin)^2} }
```

From our budget table, we calculated the numbers that Doug and Athans wanted: the simple ratio of $diff = guidance-planned; ratio.contingency = diff / planned$

We now find the maximum bound (maxbound) using the optimizer for each of the project years FY24-FY26 using the contingency values from the budget table. Use these values with calc.p to:

-   show that we get .90 for each of the original contingency values (CL.full),
-   calculate a CL for the $diff$ values.

```{r}
intr<- c(0.0, 4.0)
contingencies<- data.frame(
  year=c('FY24','FY25','FY26','FY27'), 
  full.contingency=c(.325,.958,1.07,.576),
  diff.contingency=c(.288484, .855699, .837637, 1.633)
)
voptimize<- Vectorize(function(x) { optimize(x, intr)$minimum } )
voptfunc.pert<-  Vectorize(function(x) { optfunc(.9,x,calc.qpert) } )
voptfunc.triang<-  Vectorize(function(x) { optfunc(.9,x,calc.qtriang) } )
vcalc.p.pert<- Vectorize(calc.ppert)
vcalc.p.triang<- Vectorize(calc.ptriang)

out.pert<- contingencies %>%
  mutate(maxbound=voptimize(voptfunc.pert(full.contingency))) %>%
  mutate(CL.full=vcalc.p.pert(full.contingency,maxbound)) %>%
  mutate(CL.diff=vcalc.p.pert(diff.contingency,maxbound))

out.tri<- contingencies %>%
  mutate(maxbound=voptimize(voptfunc.triang(full.contingency))) %>%
  mutate(CL.full=vcalc.p.triang(full.contingency,maxbound)) %>%
  mutate(CL.diff=vcalc.p.triang(diff.contingency,maxbound))

```

Contingency and maxbound values are in millions of dollars.
The last column, CL.diff, is the estimated confidence level given all these assumptions. Remember that CL calculations have upper limit of 1.0.

## PERT

The estimates of the confidence levels using the PERT distribution for the differences per year is in column CL.diff. 
```{r}
#| echo: false
out.pert
```


## Triangular

The estimates of the confidence levels using the triangular distribution for the differences per year is in column CL.diff. 

```{r}
#| echo: false
out.tri
```
