---
title: "R Notebook"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(stringr)
library(lubridate)

library(MAGIS100PM)

```

```{r}
datepart<-'Dec22WSCurrent'

read.my.file <- function(datepart, tab)
{
  fname<-paste('../extracted/tab_',tab,'_',datepart,'.csv',sep='')
  df <- read.csv(fname)
  df
}

adjust.date <- function(tab, col,ending) 
{ 
  name.s <- paste(col,"_start",ending,sep='')
  name.e <- paste(col,"_end",ending,sep='')
  tab[[name.s]] <- as.Date(tab[[name.s]]) 
  tab[[name.e]] <- as.Date(tab[[name.e]]) 
  tab
}

# these come from XER extractor
taskrsrc<-read.my.file(datepart, 'TASKRSRC')
rsrc<-read.my.file(datepart, "RSRC")
wbs<-read.my.file(datepart, "PROJWBS")
tasks<-read.my.file(datepart,"TASK")
roles<-read.my.file(datepart,"ROLE")
udf.type<-read.my.file(datepart,"UDFTYPE")
udf.value<-read.my.file(datepart,"UDFVALUE")

tasks<-adjust.date(tasks,"target","_date")
tasks<-adjust.date(tasks,"early","_date")
tasks<-adjust.date(tasks,"late","_date")
taskrsrc<-adjust.date(taskrsrc,"target","_date")

# this is a summary of the above out of reader.py -P -d
# it already has the wbs info merged with the tasks
all.data<-read.csv(paste("../output/alltasks_",datepart,".csv",sep=''))
all.paths<-read.csv(paste("../output/allareas_",datepart,".csv",sep=''))
all.data<-adjust.date(all.data,"target","")
all.data<-adjust.date(all.data,"early","")
all.data<-adjust.date(all.data,"late","")

all.data$cost <- as.numeric(all.data$cost)
all.data$cost[is.na(all.data$cost)] <- 0

```

Information about CPM and PERT in R:
https://cran.r-project.org/web/packages/critpath/vignettes/CPMandPERT.html

PERT charts are mentioned here, along with burndown charts:
https://www.projectmanager.com/blog/3-best-project-management-charts
https://www.projectmanager.com/guides/pert-chart

```{r}
ctc.id <- (filter(udf.type, udf_type_label=='user_text1') %>% select(udf_type_id))[[1]]
ctc.recs <- filter(udf.value, udf_type_id==ctc.id) %>% select(task_id=fk_id, ctc=udf_text)
all.data <- left_join(all.data, ctc.recs, by=join_by(task_id))
```

```{r}

all.data.labor<- filter(all.data,rsrc_type=='RT_Labor')
tmp<- taskrsrc%>% left_join(rsrc, by=join_by(rsrc_id))
tmp.2<- tmp %>% left_join(roles, by=join_by(role_id.x==role_id))
tmp.3<- tmp.2 %>% left_join(ctc.recs,by=join_by(task_id))
```


alternative way using all.data.   This is using alltasks.
What is missing: chargeable task code.   Should add task_id also for reference.
should add a switch on reader to generate this alltasks file, and decorate with the "datepart".



```{r}

date.list <- function(a,b,c)
{
  tmp<-seq.Date(from=a, to=b, by='week')
  data.frame(d=floor_date(tmp,unit="week",week_start=7),hours=c/(length(tmp)))
}

date.list.days <- function(a,b,c)
{
  tmp<-seq.Date(from=a, to=b, by='day')
  data.frame(d=floor_date(tmp,unit="day",week_start=7),hours=c/(length(tmp)))
}

```

```{r}

plot.sum <- function(data, grp)
{
a.2<- select(data, s=target_start, e=target_end, d=dur, g=grp) %>% rowwise() %>% mutate(dl=list(date.list(s,e,d)))
a.2<- unnest(a.2,cols=c(dl),names_sep='.') %>% arrange(g,s)
tot.hours.tmp<- group_by(a.2,g,dl.d) %>% summarise(sum=sum(dl.hours),.groups='keep')
tot.hours<- arrange(tot.hours.tmp,g,dl.d) %>% group_by(g) %>% mutate(csum=cumsum(sum))

print(ggplot(tot.hours,aes(x=dl.d, y=csum,colour=as.factor(g))) + geom_line())
print(ggplot(tot.hours,aes(x=dl.d, y=sum,colour=as.factor(g))) + geom_line())
tot.hours
}

plot.sum2 <- function(data, grp)
{
a.2<- filter(data,rsrc_type.x=='RT_Labor')%>%
  select( s=target_start_date, e=target_end_date, d=target_qty, r=remain_qty, g=grp) %>%
  filter(!is.na(g))%>% 
  rowwise() %>% mutate(dl=list(date.list(s,e,d)))

a.2<- unnest(a.2,cols=c(dl),names_sep='.') %>% arrange(g,s)
tot.hours.tmp<- group_by(a.2,g,dl.d) %>% summarise(sum=sum(dl.hours),.groups='keep')
tot.hours<- arrange(tot.hours.tmp,g,dl.d) %>% group_by(g) %>% mutate(csum=cumsum(sum))

print(ggplot(tot.hours,aes(x=dl.d, y=csum,colour=as.factor(g))) + geom_line())
print(ggplot(tot.hours,aes(x=dl.d, y=sum,colour=as.factor(g))) + geom_line())
tot.hours
}

```

```{r}

plot.sum3 <- function(data, grp, name)
{
a.2<- filter(data,rsrc_type.x=='RT_Labor')%>%
  select( task_id=task_id,s=target_start_date, e=target_end_date, d=target_qty, r=remain_qty, g=grp) %>%
  filter(!is.na(g)&str_detect(g,name))%>% 
  rowwise() %>% mutate(dl=list(date.list(s,e,d)))

#view(filter(data,rsrc_type.x=='RT_Labor')%>%
#  select( task_id=task_id,s=target_start_date, e=target_end_date, d=target_qty, r=remain_qty, g=grp) %>%
#  filter(!is.na(g)&str_detect(g,name)))
a.2<- unnest(a.2,cols=c(dl),names_sep='.') %>% arrange(g,s)
# %>% distinct(g,dl.d,.keep_all=TRUE)
#view(a.2)
#noah<-a.2%>%filter(dl.d==as.Date("2023-06-19"))#%>%group_by(g)%>%summarise(summ=sum(dl.hours))
#view(noah)
#noah<-noah%>%left_join(select(tasks,task_id,task_code),by=join_by(task_id))
#view(noah)

tot.hours.tmp<- filter(a.2,s>as.Date('2022-12-01'))%>%group_by(g,dl.d) %>%
  summarise(sum=sum(dl.hours),.groups='keep') 
#view(tot.hours.tmp)

tot.hours<- arrange(tot.hours.tmp,g,dl.d) %>% group_by(g) %>% 
  mutate(csum=cumsum(sum))
#view(tot.hours)

t.1<-ggplot(tot.hours,aes(x=dl.d, y=csum,colour=as.factor(g))) +
  scale_x_date(date_breaks='1 month', date_labels = "%b %y") + 
  theme(axis.text.x = element_text(angle = 90)) +
  geom_step()
t.2<-ggplot(tot.hours,aes(x=dl.d, y=sum,colour=as.factor(g))) +
  scale_x_date(date_breaks='1 weeks', date_labels = "%d %b %y") +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_step() + facet_grid(vars(g), scales="free_y")
print(t.1)
print(t.2)
ggsave(t.2, filename="hours.pdf",units="in", height=10, width=24, device="pdf")
print(getwd())
tot.hours
}

```

```{r}
#plot.sum2(tmp.2,'role_name')
#plot.sum2(tmp.2,'rsrc_short_name')
#total.hours <- plot.sum3(tmp.2, 'role_name', "Noah")
#total.hours <- plot.sum3(tmp.2, 'role_name', "Chappa")
#total.hours <- plot.sum3(tmp.2, 'role_name', "Funk|Noah|Chappa|Arv|Ron|Santu|Lucy")
#total.hours <- plot.sum3(tmp.2, 'role_name', ".*")
#total.hours <- plot.sum3(tmp.2,'rsrc_name','Operations')
total.hours <- plot.sum3(tmp.2,'rsrc_name','Engineer|Operation|Design|Draft')
#total.hours <- plot.sum3(tmp.2,'rsrc_name','.*')
```


```{r}
#tot.sum<-plot.sum(all.data.labor, 'area')
 # + facet_grid(rows=vars(area))


```

Don't run this one


all.data.2021<-filter(all.data, year(target_start)>2021)
all.data.2021$g=as.numeric(as.factor(all.data.2021$group))
gp<-ggplot(all.data.2021, aes(xmin = as.Date(target_start), xmax = as.Date(target_end), 
                   y=group,# ymin = g, ymax = g+.8, 
                   fill = category)) +
  geom_rect(aes(ymin = g, ymax = g+.8)) +
  scale_y_discrete("group") +
  scale_x_date(date_breaks='1 month', date_labels = "%b %y") +
  theme(axis.text.x = element_text(angle = 90)) + 
  geom_text(aes(x = as.Date(target_start), label = wbs), nudge_x=39.6, nudge_y=.2, size=3)

Original way ...

dates.seq<- seq.Date(from = as.Date('2022-06-06'), to = max(tasks$target_end_date), by = 'weeks')
a.1 <- hist(tasks$target_start_date, "weeks", plot=FALSE)

date.list <- function(a,b,c)
{
  data.frame(d=seq.Date(from=a, to=b, by='weeks'),hours=c)
}

a.2<- select(tasks, s=target_start_date, e=target_end_date, d=target_drtn_hr_cnt) %>% rowwise() %>% mutate(dl=list(date.list(s,e,d)))
a.2<- unnest(a.2,cols=c(dl),names_sep='.') %>% arrange(s)
tot.hours<- group_by(a.2,dl.d) %>% summarise(sum=sum(dl.hours))
tot.hours<- arrange(tot.hours, dl.d) %>% mutate(csum=cumsum(sum))

# ggplot(tot.hours,aes(x=tot.hours$dl.d, y=tot.hours$csum)) + geom_line()



```{r}
by.day<- filter(tmp.2,rsrc_type.x=='RT_Labor') %>%
  select( task_id=task_id,s=target_start_date, e=target_end_date, dt=target_qty, r=remain_qty, g=role_name) %>%
  filter(!is.na(g)&str_detect(g,".*")) %>% 
  rowwise() %>% mutate(dl=list(date.list.days(s,e,dt)))

by.day2<- unnest(by.day,cols=c(dl),names_sep='.') %>% arrange(g,s) %>%
  mutate(week=floor_date(dl.d,unit="week",week_start=1)) 
```

by.day3<- by.day2 %>% filter(s>as.Date('2022-12-01')) %>%
  group_by(g,week) %>% summarise(sum=sum(dl.hours),.groups='keep')

t.2<-ggplot(by.day3,aes(x=week, y=sum,colour=as.factor(g))) +
  scale_x_date(date_breaks='1 weeks', date_labels = "%d %b %y") +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_step() + facet_grid(vars(g), scales="free_y")

print(t.2)
ggsave(t.2, filename="hours.pdf",units="in", height=10, width=24, device="pdf")



# &target_end<as.Date("2023-03-01")

tmp<- all.data%>%
  filter((area>9 | area==1))%>%
  arrange(ctc,target_end)%>%
  group_by(ctc)%>%
  summarise(tot=sum(cost))
  #reframe(tot=cumsum(cost),e=target_end, s=target_start)


```{r}
by.day<- tmp.3 %>%
  filter(rsrc_type.x=='RT_Labor') %>%
  select( task_id=task_id,s=target_start_date, e=target_end_date, dt=target_qty, r=remain_qty, g=ctc) %>%
  filter(!is.na(g)&str_detect(g,".*")) %>% 
  rowwise() %>% mutate(dl=list(date.list.days(s,e,dt)))

by.day2<- unnest(by.day,cols=c(dl),names_sep='.') %>% arrange(g,s) %>%
  mutate(week=floor_date(dl.d,unit="week",week_start=1)) 

by.day3<- by.day2 %>% 
  arrange(g,week)%>%
  group_by(g) %>% mutate(sum=cumsum(dl.hours),.groups='keep')

t.2<-ggplot(by.day3,aes(x=week, y=sum,colour=as.factor(g))) +
  scale_x_date(date_breaks='1 weeks', date_labels = "%d %b %y") +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_step() + facet_grid(vars(g), scales="free_y")

print(t.2)
ggsave(t.2, filename="hours2.pdf",units="in", height=10, width=24, device="pdf")

```

```{r}
# temporary
#first.week<-as.Date('2023-03-05')

# magic dates - Kronos and scheduled hours almost match in this range.
# Increasing first.week date by one day makes scheduled hours go higher than logged hours.
# It gets much worse as first.week approaches last.week.
first.week<-as.Date('2022-05-08')
last.week<-as.Date('2023-03-08')

#  There are no scheduled hours in this range of dates, but Kronos logged 6131 hours.
#first.week<-as.Date('2019-01-01')
#last.week<-as.Date('2022-05-09')

# Later data
#first.week<-as.Date('2022-12-20')
#last.week<-as.Date('2023-03-08')


#first.week<-as.Date('2019-01-01')
#last.week<-as.Date('2022-10-06')

first.week<-as.Date('2023-10-01')
last.week<-as.Date('2024-09-30')

by.day<- tmp.3 %>%
  filter(rsrc_type.x=='RT_Labor') %>%
  select( task_id=task_id,s=target_start_date, e=target_end_date, dt=target_qty, r=remain_qty, g=rsrc_short_name) %>%
  filter(!is.na(g)&str_detect(g,".*")) %>% 
  rowwise() %>% mutate(dl=list(date.list.days(s,e,dt)))

by.day2<- unnest(by.day,cols=c(dl),names_sep='.') %>% arrange(g,s) %>%
  mutate(week=floor_date(dl.d,unit="week",week_start=1)) 

by.day3<- by.day2 %>% 
  filter(week<last.week & week>first.week)%>%
  group_by(g,week) %>% summarise(hsum=sum(dl.hours))
print('-')

by.week4<- by.day3 %>%
  arrange(g,week)%>%
  group_by(g) %>% mutate(csum=cumsum(hsum))

tmp.ctc.hours<-by.day3%>%
  filter(week<last.week & week>first.week)%>%
  group_by(g) %>%summarise(tot=sum(hsum)) 
print('-')

by.kronos4<- all.charges%>%
  filter(Timecard.Start<last.week & Timecard.Start>first.week)%>%
  select(Last.Name, taskname, Timecard.Start, Hours)%>%
  arrange(taskname, Timecard.Start)%>%
  group_by(taskname) %>% mutate(ksum=cumsum(Hours))

j.ctc<- bind_rows( distinct(by.kronos4,taskname), distinct(select(by.week4,taskname=g), taskname))
j.ctc$taskname.code<- str_detect(j.ctc$taskname, "Proj") * 1 + 
  str_detect(j.ctc$taskname, "Civil") * 2 +
  str_detect(j.ctc$taskname, "Proto") * 3 +
  str_detect(j.ctc$taskname, "Research") * 4 +
  str_detect(j.ctc$taskname, "Network") * 5 +
  str_detect(j.ctc$taskname, "Qual") * 6

j.ctc$rsrc.code<- case_when(
  str_detect(j.ctc$taskname,"COORD")~'TECH', 
  str_detect(j.ctc$taskname,"APDEV")~'ENG', 
  str_detect(j.ctc$taskname,"DRIVE")~'TECH', 
  str_detect(j.ctc$taskname,"TECH")~'TECH', 
  str_detect(j.ctc$taskname,"DESIGN")~'ENG', 
  str_detect(j.ctc$taskname,"PHYST")~'SCI', 
  str_detect(j.ctc$taskname,"MACHIN")~'TECH', 
  str_detect(j.ctc$taskname,"DRAFT")~'TECH', 
  str_detect(j.ctc$taskname,"METRO")~'TECH', 
  str_detect(j.ctc$taskname,"SPCLST")~'TECH', 
  str_detect(j.ctc$taskname,"PRJ")~'ADMIN', 
  str_detect(j.ctc$taskname,"EXP_RA")~'RA', 
  str_detect(j.ctc$taskname,"SAFE")~'TECH', 
  TRUE~"NONE"
  )

by.kronos4<- left_join(by.kronos4, j.ctc, by=join_by(taskname))  
by.week4<- left_join(by.week4, j.ctc, by=join_by(g==taskname))

tmp.kronos.hours<-all.charges%>%
  filter(Timecard.Start>first.week & Timecard.Start<last.week)%>%
  group_by(taskname)%>%summarise(tot=sum(Hours))

by.both4<- full_join(by.week4, by.kronos4, by=join_by(taskname.code, week==Timecard.Start))

#view(tmp.ctc.hours)
#view(tmp.kronos.hours)

s.k<-sum(tmp.kronos.hours$tot)
s.c<-sum(tmp.ctc.hours$tot)
print(s.k)
print(s.c)
print(s.k-s.c)
```
```{r}
t.2<-ggplot(by.week4,aes(x=week, y=hsum,colour=as.factor(g))) +
  scale_x_date(date_breaks='1 weeks', date_labels = "%d %b %y") +
  theme(axis.text.x = element_text(angle = 90)) +
  geom_step() + facet_grid(vars(g), scales="free_y")

#t.2<-ggplot(by.both4,aes(x=week, y=csum,colour=as.factor(g))) +
#  scale_x_date(date_breaks='1 weeks', date_labels = "%d %b %y") +
#  theme(axis.text.x = element_text(angle = 90)) +
#  geom_step() + facet_grid(vars(g), scales="free_y")

print(t.2)
ggsave(t.2, filename="hours3.pdf",units="in", height=10, width=24, device="pdf")

```

