---
title: "R Notebook"
output:
  html_notebook: default
  pdf_document: default
---

```{r message=FALSE, warning=FALSE}
#```{r}
library(tidyverse)
library(ggplot2)
library(readxl)
library(stringr)
library(lubridate)

library(MAGIS100PM)

```

EXAMPLES of how to adjust date columns:
names(all.charges) <- make.names(colnames(all.charges))
tmp<-as.POSIXlt(all.charges$Timecard.Start)
all.charges <- all.charges %>% mutate(year=tmp$year-100+2000,month=tmp$mon)

unlist(as.POSIXlt(all.charges$Timecard.End[5001]))
sec   min  hour  mday   mon  year  wday  yday isdst 
  0     0     0    22     4   122     0   141     0 
  

```{r}
#datepart<-'Dec2022FY24Scenario'
#datepart<-'Dec2022FY24ScenarioUpdated' # with delayed M&S
#datepart<-'Dec2022FY23' # limited to 5.4M spending
#datepart<-'Dec2022StatusInput'
#datapart<-'Dec2022Current'
#datepart<-'Dec22WSCurrent'
datepart<-'current'
#datepart<-'previous'

read.my.file <- function(datepart, tab)
{
  fname<-paste('extracted/tab_',tab,'_',datepart,'.csv',sep='')
  df <- read.csv(fname)
  df
}

adjust.date <- function(tab, col,ending) 
{ 
  name.s <- paste(col,"_start",ending,sep='')
  name.e <- paste(col,"_end",ending,sep='')
  tab[[name.s]] <- as.Date(tab[[name.s]]) 
  tab[[name.e]] <- as.Date(tab[[name.e]]) 
  tab
}

# these come from XER extractor
taskrsrc<-read.my.file(datepart, 'TASKRSRC')
taskpred<-read.my.file(datepart, 'TASKPRED')
rsrc<-read.my.file(datepart, "RSRC")
wbs<-read.my.file(datepart, "PROJWBS")
tasks<-read.my.file(datepart,"TASK")
roles<-read.my.file(datepart,"ROLE")
udf.type<-read.my.file(datepart,"UDFTYPE")
udf.value<-read.my.file(datepart, "UDFVALUE")
# this is a summary of the above out of reader.py -P -d
all.data<-read.csv(paste("output/alltasks_",datepart,".csv",sep=''))
#all.paths<-read.csv(paste("output/allareas_",datepart,".csv",sep=''))
all.data<-adjust.date(all.data,"target","")
all.data<-adjust.date(all.data,"early","")
all.data<-adjust.date(all.data,"late","")

```

```{r}
#path.data <- left_join(all.paths, all.data, by=join_by(code))
```


Sequence is 
Find line in TASKRSRC, first two columns are IDs: taskrsrc_id, task_id
Find task_id in TASK: there is a task ID and task name here, and task_id,proj_id,wbs_id.
Find wbs_id in PROJWBS: the name of this area is found here

#```{r}
#view(all.data%>%select(name, wbs, category, group, wbs_high, wbs_low))

tmp<-filter(path.data, year(target_start)>2021 & type!='Q' & wbs!='01.01')
tmp$g=as.numeric(as.factor(tmp$group))
tmp$a=as.numeric(as.factor(tmp$area))
tmp$p=as.numeric(as.factor(tmp$path))

# started with label=code
# y_discrete = "group"
# y = group
# ymin = g, ymax = g+.8
gp<-ggplot(tmp, aes(xmin = as.Date(target_start), xmax = as.Date(target_end), 
                   y=as.factor(path),# ymin = g, ymax = g+.8, 
                   fill = category)) +
  geom_rect(aes(ymin = p, ymax = p+.8)) +
  scale_y_discrete("path") +
  scale_x_date(date_breaks='1 month', date_labels = "%b %y") +
  theme(axis.text.x = element_text(angle = 90)) + 
  geom_text(aes(x = as.Date(target_start), label = wbs), nudge_x=39.6, nudge_y=.2, size=3)#, check_overlap = TRUE)

ggsave(gp, filename="vs.pdf",units="in", height=10, width=24, device="pdf")
print(gp)
#```

```{r}
sched <- tasks %>% left_join(wbs, by=join_by(wbs_id)) %>% select( task_id, target_start_date, target_end_date, task_code, task_name, wbs_id, wbs_name, wbs_short_name) %>% arrange(target_start_date)
```


```{r}
costs <- filter(taskrsrc,target_cost>0) %>% left_join(tasks,by=join_by(task_id))%>%left_join(wbs, by=join_by(wbs_id)) %>% select( task_id, target_cost, cost_per_qty, target_start_date.x, target_end_date.x, task_code, task_name, wbs_id, wbs_name, wbs_short_name) %>% arrange(target_start_date.x)
#view(costs)
```


#```{r}
group.cat <- ggplot(all.data,aes(x=group, y=category)) + theme(axis.text.x = element_text(angle = 90)) + geom_count()
group.area <- ggplot(all.data,aes(x=group, y=wbs_high)) + theme(axis.text.x = element_text(angle = 90)) + geom_count()
cat.area <- ggplot(all.data,aes(x=category, y=wbs_high)) + theme(axis.text.x = element_text(angle = 90)) + geom_count()
print(group.cat)
print(group.area)
print(cat.area)
#```

```{r}
stop.code.list <- read.csv("input/code_list.csv",header=TRUE)
```

The lines that are wrong values are:

179259425 A1701AA10   rsrc_type = RT_Equip for the 240 in taskrsrc
179259423 A1701N10    Same thing is true for this one, for the 240

X Now task_id 179259445 is missing!!! (value of 60 hours) task_code A1803770

A1802700 is missing
A1803460 seems to be missing
A1803770 is missing


```{r}
# get all the tasks that match our task_code
stopped.tasks <- left_join(stop.code.list, tasks, by=join_by(task_code)) %>% select(task_id, task_code, target_work_qty,rsrc_id, task_name)

# get all the taskrsrc records that match our task_id
stopped.taskrsrc <- left_join(stopped.tasks, filter(taskrsrc,rsrc_type=='RT_Labor'),multiple='all', by=join_by(task_id)) %>% select(task_id, task_code, rsrc_id.x, rsrc_id.y, target_qty, target_work_qty, rsrc_type)

stopped.rsrcs <- stopped.taskrsrc %>% left_join(filter(rsrc,rsrc_type=='RT_Labor'),by=join_by(rsrc_id.y==rsrc_id)) %>% select(task_id, task_code, rsrc_name, rsrc_id.y, target_qty, target_work_qty, rsrc_name, rsrc_type.x) %>% filter(!is.na(target_qty))


hours.sum <-select(stopped.rsrcs,rsrc_id.y,task_code,rsrc_name,target_qty) %>% group_by(rsrc_name) %>% summarise(total.hours=sum(target_qty))

```


```{r}
alltask.lv <-read_excel("output/alltasks LV edit.xlsx") 
alltask.lv <- select(alltask.lv, code, category, group, 'New Category', 'New Group', 'Label Type', LABEL) %>% arrange(code)
names(alltask.lv)<-c('code','old.category','old.group','new.category','new.group','label.type','label')

new.ones.grp<-!is.na(alltask.lv$new.group)
new.ones.cat<-!is.na(alltask.lv$new.category)
alltask.lv<-mutate(alltask.lv, category=alltask.lv$old.category, group=alltask.lv$old.group)
alltask.lv$category[new.ones.cat]<-alltask.lv$new.category[new.ones.cat]
alltask.lv$group[new.ones.grp]<-alltask.lv$new.group[new.ones.grp]
```

reports for 
What activities are ongoing now? -> now within [start, end]
What was supposed to start? -> status==TK_NotStart  and planned_start < now
What was supposed to end? -> status==started and planned_end < now
What is coming up next? -> status==not started and planned_start within [now, now+1 month]

What has been active for >6 months
What has a gap between target start and late start of greater than X months?
What has a gap between target end and late end of greater than X months?


```{r}

now <- Sys.Date()

tot.costs <-  taskrsrc %>% group_by(task_id) %>% summarise(total_cost=sum(target_cost),.groups='drop')
all.data <- all.data %>% left_join(tot.costs, by=join_by(task_id))

# target interval
target <- interval(all.data$target_start, all.data$target_end)
```

```{r}
# start date interval
start.interval <- interval('2023-09-01', '2023-08-30')
start.interval.Q4 <- interval('2023-09-01', '2023-12-30')
# start date interval
end.interval <- interval('2023-11-01', '2024-11-01')
late.interval <- interval('2025-09-01', '2025-12-31')
full.interval <- interval('2023-10-01', '2028-12-30')

active <- all.data[now %within% target,] %>% arrange(desc(target_start))
full.one <- all.data[all.data$target_start %within% full.interval,] %>% arrange(desc(target_start))
starting.Q3 <- all.data[all.data$target_start %within% start.interval,] %>% arrange(desc(target_start))
starting.Q4 <- all.data[all.data$target_start %within% start.interval.Q4,] %>% arrange(desc(target_start))
latest.Q4 <- all.data[all.data$target_start %within% late.interval,] %>% arrange(desc(target_start))
ending.Q4 <- all.data[all.data$target_end %within% end.interval,] %>% arrange(desc(target_end))
no.start <- all.data %>% filter(status=='TK_NotStart' & target_start<now)
should.end <- all.data %>% filter(status=='TK_Active' & target_end<now)
up.next <- all.data %>% filter(status=='TK_NotStart' & target_start %within% interval(now,now+months(1)))
start.gap <- all.data %>% filter((late_start-target_start)>months(9))
end.gap <- all.data %>% filter((late_end-target_end)>months(9))
```


```{r}
#tmp<-active%>% #ending.Q4%>%
tmp<-full.one%>% #ending.Q4%>%
#tmp<-latest.Q4%>% #ending.Q4%>%
  #filter(target_start<as.Date("2026-10-01")&target_start>as.Date("2022-07-01")&(area>10|area==1))
  filter(target_start>as.Date('2023-05-01'))%>%
  filter(str_detect(name,"eview"))
  #filter(total_cost>=0&(area>10|area==1)) # %>% filter(rsrc_type=='RT_Labor') #&total_float>=0)

# size was 1.8 and 1.5 originally
# size changed to 2.8 and 2.5
# text element_text size=8 originally
# blue linewidth 1.0 originally

gp<-ggplot(tmp, aes( 
                   y=reorder(code,target_start)
                   #y=reorder(code,total_cost)
                   )) +
  geom_linerange(aes(xmin = early_start, xmax = early_end),colour='red',position=position_nudge(y=0.0)) +
  geom_linerange(aes(xmin = late_start, xmax = late_end), colour='green',position=position_nudge(y=0.0)) +
  geom_linerange(aes(xmin = target_start, xmax = target_end), colour='blue', linewidth=.70) +
  geom_text(aes(hjust='left',x = target_start, label = paste(total_cost,name,sep=":")), nudge_x=9.6, nudge_y=.4, size=1.8) +
  geom_text(aes(hjust='left',x = late_end, label = paste(free_float, total_float, sep='/')), nudge_x=9.6, nudge_y=.4, size=1.5) +
  #geom_point(aes(x=now)) +
  #scale_y_discrete("code") +
  scale_x_date(date_breaks='1 month', date_labels = "%b %y") +
  theme(axis.text.x = element_text(angle = 90),axis.text=element_text(size=6)) +
  labs(x="Target Start Date", y="Activity", fill="role")
print(gp)

ggsave(gp, filename="activeX.pdf",units="in", height=10, width=24, device="pdf")

```

```{r}
tmp<-select(active,code)[,1]
tmp2<-tasks[(tasks$task_code %in% tmp),]
tmp2.1<-tmp2 %>% filter((target_drtn_hr_cnt-remain_drtn_hr_cnt)==0 ) %>% select(task_code, remain_drtn_hr_cnt, target_drtn_hr_cnt, task_name, task_id)

march1<-as.Date("2023-03-01")
tmp2.2<-active%>%
  filter(area>10|area==1)%>%
  filter(rsrc_type!='-'& target_start<as.Date("2022-08-31"))%>%
  select(code, name, dur, target_start, target_end, task_id)%>%
  mutate(perc=as.numeric(march1-target_start)/as.numeric(target_end-target_start)) %>%
  arrange(target_start)

tmp2.3<-tmp2.2 %>% 
  left_join(taskrsrc, multiple='all', by=join_by(task_id)) %>% 
  left_join(rsrc, by=join_by(rsrc_id)) %>% 
  select(code,name,dur,target_start,target_end, rsrc_id, target_qty, remain_qty, rsrc_name, perc)

#view(tmp2.3)

```



#```{r}

gp2<-ggplot(active%>%filter(area>10|area==1), 
            aes( colour=as.factor(area), y=reorder(code,target_start))
            ) +
  geom_linerange(aes(xmin = target_start, xmax = target_end), linewidth=1.0)+ #, colour='blue') +
  #scale_y_discrete("code") +
  scale_x_date(date_breaks='1 month', date_labels = "%b %y") +
  theme(axis.text.x = element_text(angle = 90),axis.text=element_text(size=8)) #+ 
print(gp2)
ggsave(gp2, filename="active2X.pdf",units="in", height=10, width=24, device="pdf")
#```

```{r}

tmp<- all.data%>% 
  mutate(doe_scope=ifelse(area>10|area<2,"DOE-scope","in-kind"), short_name=str_sub(str_replace(str_remove(name,"Milestone"),"Procurement","Proc"),end=40)) %>%
  filter(type=='M' & target_end>as.Date('2023-10-01')) #& area<10 & area>1), 
  #filter(target_end>as.Date('2023-10-01')) #& str_detect(name,"instal")) #& area<10 & area>1), 

  #geom_point(aes(x=late_end)) +
  #geom_text(aes(hjust='left',x = target_end, label = paste(total_cost,name,sep=":")), nudge_x=9.6, nudge_y=.4, size=1.8) +
  #geom_text(aes(hjust='left',x = late_end, label = paste(free_float, total_float, sep='/')), nudge_x=9.6, nudge_y=.4, size=1.5, check_overlap = TRUE) +
  #scale_y_discrete(sec.axis=dup_axis(~total_float))+


gp3<-ggplot(
  tmp,
  aes( colour=as.factor(wbs_high), y=reorder(code,target_start))
  ) +
  geom_linerange(aes(xmin = target_end, xmax = late_end), linewidth=.10)+ #, colour='blue') +
  geom_linerange(aes(xmin = early_start, xmax = target_end), linewidth=.10)+ #, colour='blue') +
  geom_point(aes(x=target_end),size=5) +
  geom_text(aes(hjust='left',x = target_end, label = short_name), 
            nudge_x=9.6, nudge_y=.4, size=1.8) +
  geom_text(aes(hjust='right',x=as.Date(max(target_end))+months(3), label = paste(free_float, total_float, sep='/')), 
            nudge_y=.4, size=1.8, check_overlap = TRUE) +
  #facet_grid(rows=vars(doe_scope), scales = "free_y")+
  scale_x_date(date_breaks='1 month', date_labels = "%b %y") +
  theme(axis.text.x = element_text(angle = 90, size=24),
        axis.text=element_text(size=13),
        axis.title=element_text(size=30), 
        legend.title=element_text(size=30), 
        legend.text=element_text(size=16),
        strip.text.y=element_text(size=22)) +
  labs(x="Target End Date", y="Milestone", colour="WBS area")
print(gp3)
ggsave(gp3, filename="milestonesX.pdf",units="in", height=30, width=24, device="pdf")
ggsave(gp3, filename="milestonesX.png",units="in", height=26, width=24, device="png")
```

This is temporary code:
```{r}
#tmp.current <- all.data
#tmp.previous <- all.data

FY26.interval <- interval('2025-10-01', '2026-09-30')
FY2425.interval <- interval('2023-10-01', '2025-09-30')
FY24.interval <- interval('2023-10-01', '2024-09-30')
FY25.interval <- interval('2024-10-01', '2025-09-30')

tmp.both<- left_join(tmp.current, tmp.previous, by=join_by(code),suffix=c(".cur",".prv"))
tmp.diff<- tmp.both %>% select(code, name.cur, dur.cur, dur.prv, target_start.cur, target_start.prv, target_end.cur, target_end.prv, total_float.cur, total_float.prv, total_cost.cur, cost.cur, wbs.cur, group.cur,category.cur) %>% mutate(dur.diff=dur.cur-dur.prv, float.diff=total_float.cur-total_float.prv, dd.task=dur.cur==dur.prv*2)
tmp.filtered<- tmp.diff %>% filter((target_start.cur %within% FY2425.interval | target_end.cur %within% FY2425.interval))%>% mutate(end.diff=target_end.cur - target_end.prv,start.diff=target_start.cur - target_start.prv) #%>% filter(dur.x!=0)

write.csv(tmp.filtered, "differences.csv")

tmp.filtered %>% filter((target_start.cur %within% FY24.interval | target_end.cur %within% FY24.interval)) %>% summarise(tcost=sum(total_cost.cur))

#tmp<- tasks%>% filter(as.Date(cstr_date)<as.Date('2023-04-03')&cstr_type=='CS_MSOA')%>%select(task_code, task_name, cstr_date, cstr_type)%>%arrange(cstr_date)
```

```{r}
#write.csv(
#  tasks %>% filter(target_start_date>as.Date('2023-03-01')&target_end_date<as.Date('2023-10-01)'))%>%select(task_name, task_code, target_start_date, target_end_date),
#  "fy23_tasks.csv")

getwd()
write.csv(
  all.data%>%filter(target_start>as.Date('2024-09-30')&target_end<as.Date('2027-12-01)'))%>%select(wbs, area,name, code, target_start, target_end, category, group),
  "../docs_pm/all_tasksX.csv")

# view(all.data %>% mutate(thing=target_end-target_start)%>% select(code, area, name, thing))

# look at this one.   Ariel is in the mix. 
# view(filter(all.data,area<11)%>%left_join(filter(udf.value,udf_type_id==3886), join_by(task_id==fk_id))%>%select(code, target_start, target_end, udf_text, area, wbs)%>%group_by(wbs,udf_text)%>%summarise(mi=min(target_start),ma=max(target_end))%>% arrange(wbs,ma))

in.kind.person<- filter(all.data,area>1)%>%
  mutate(doe_scope=ifelse(area>10|area<2,"DOE-scope","in-kind"))%>%
  left_join(filter(udf.value,udf_type_id==3886), join_by(task_id==fk_id))%>%
  select(doe_scope, code, target_start, target_end, late_start, late_end, person=udf_text, area, wbs_high, wbs)#%>%

tmp.w <- in.kind.person %>% distinct(area,wbs_high)

in.kind.max<- in.kind.person %>% 
  group_by(doe_scope,area,wbs,person)%>%
  summarise(min_start_date=min(target_start),max_end_date=max(target_end),min_late_start=min(late_start),max_late_end=max(late_end))%>% 
  left_join(tmp.w,by=join_by(area))%>%
  arrange(area,max_end_date)
  #arrange(max_end_date)

write.csv(in.kind.max,"in_kind_max_date.csv")

gp4<-ggplot(
  in.kind.max,
  aes( colour=as.factor(person), 
       #y=as.factor(area) 
       y=reorder(paste(area,"/",wbs_high), max_end_date)
  )
  ) +
  geom_linerange(aes(xmin = max_end_date, xmax = max_late_end), linewidth=.10, position=position_dodge2(width=.8))+ #, colour='blue') +
  geom_point(aes(x=max_end_date),position=position_dodge2(width=.8)) +
  #geom_text(aes(hjust='left',x = max_end_date, label = person)) +
  facet_grid(rows=vars(doe_scope), scales = "free_y")+
  scale_x_date(date_breaks='1 month', date_labels = "%b %y") +
  theme(axis.text.x = element_text(angle = 90))+ #,axis.text=element_text(size=6)) +
  labs(x="Target end date (dot) and late end date (line)", y="High-level WBS name", colour="Person responible")
print(gp4)
ggsave(gp4, filename="in_kind_dates.pdf",units="in", height=10, width=24, device="pdf")
ggsave(gp4, filename="in_kind_dates.png",units="in", height=10, width=24, device="png")

```


```{r}
tmp<-full.one%>% 
  #filter(area%in%c(2,4,5,6,7,9,10)) # Jason
  filter(area%in%c(8)) # Ian
  #filter(area%in%c(3)) # Tim

gp<-ggplot(tmp, aes( 
                   y=reorder(code,target_start)
                   )) +
  geom_linerange(aes(xmin = early_start, xmax = early_end),colour='red',position=position_nudge(y=0.0)) +
  geom_linerange(aes(xmin = late_start, xmax = late_end), colour='green',position=position_nudge(y=0.0)) +
  geom_linerange(aes(xmin = target_start, xmax = target_end), colour='blue', linewidth=.70) +
  geom_text(aes(hjust='left',x = target_start, label = paste(total_cost,name,sep=":")), nudge_x=9.6, nudge_y=.4, size=1.8) +
  geom_text(aes(hjust='left',x = late_end, label = paste(free_float, total_float, sep='/')), nudge_x=9.6, nudge_y=.4, size=1.5) +
  #geom_point(aes(x=now)) +
  #scale_y_discrete("code") +
  scale_x_date(date_breaks='1 month', date_labels = "%b %y") +
  theme(axis.text.x = element_text(angle = 90),axis.text=element_text(size=6)) +
  labs(x="Target Start Date", y="Activity", fill="role")
print(gp)

ggsave(gp, filename="active_Ian.pdf",units="in", height=10, width=24, device="pdf")

```
