---
title: "R Notebook"
output: html_notebook
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(stringr)
library(lubridate)


FY <- function(year)
{
  function(rec)
  {
    (rec$year==(year-1) & rec$month>=9)|(rec$year==year & rec$month<9)
  }
}

fiscal.yr<-function(year, month)
{
  year <- year + ifelse(month>=9,1,0)
}
fiscal.year<-function(recs)
{
  fiscal.yr(recs$year, recs$month)
}
fiscal.month<-function(recs)
{
  recs$month + ifelse(recs$month>=9, -9, +3)
}
```

'Kronos Summary Report (By Task)_Q1903_20230205.xlsx'
'Kronos Summary Report (By Task)_Q1903_20230130.xlsx'

Home Project	Home Task	Transfer Project	Transfer Task	Activity Name	Activity Description	Department	Fermi ID	Last Name	First Name	Timecard Start	Timecard End	Transaction Date	Job Functional Code	Hours	Expenditure Type	He Indicator	Historical Date	Project	Charge Task Code	DSC	WBS Name	Full Name	WBS	Timecard End : Month	Timecard End: Year	Units	Task Name	Long Task Name	Description	Function Role	Function Category

Columns 1, 2, and 18 need to be forced to text type
there are a total of 32 columns

Pull out year and month from timecard start dates
Add these columns to the charges dataframe

```{r}

chg.cols = rep('guess',32)
chg.cols[1]='text'
chg.cols[2]='text'
chg.cols[18]='text'

c3 <- read_excel('../../Kronos Summary Report (By Task)_Q1903_20230305.xlsx', col_types=chg.cols)
c2 <- read_excel('../../Kronos Summary Report (By Task)_Q1903_20230219.xlsx', col_types=chg.cols)
c1 <- read_excel('../../Kronos Summary Report (By Task)_Q1903_20230205.xlsx', col_types=chg.cols)
c0 <- read_excel('../../Kronos Summary Report (By Task)_Q1903_20230130.xlsx', col_types=chg.cols)
all.charges <- bind_rows(bind_rows(bind_rows(c0,c1),c2),c3)
names(all.charges) <- make.names(colnames(all.charges))

tmp<-as.POSIXlt(all.charges$Timecard.Start)
all.charges <- all.charges %>% mutate(year=tmp$year-100+2000,month=tmp$mon)

# add a fiscal year field
all.charges$fiscal.year <- fiscal.year(all.charges)
all.charges$fiscal.month <- fiscal.month(all.charges)
```

```{r}
plot.sum <- function(data, grp)
{
tmp<- select(data, d=Timecard.Start, Hours=Hours, g=grp)
tmp<- group_by(tmp,g, d) %>% summarise(sum=sum(Hours),.groups='keep')
tot.hours<- arrange(tmp,g,d) %>% group_by(g) %>% mutate(csum=cumsum(sum))

print(ggplot(tot.hours,aes(x=d, y=csum,colour=as.factor(g))) + geom_line())
print(ggplot(tot.hours,aes(x=d, y=sum,colour=as.factor(g))) + geom_line())
}

plot.sum(all.charges, 'Task.Name')
```


Budget spreadsheet
'MAGIS FY23 Budget for cuts v8.xlsx'

Task Name and Notes contain the task code names that we need.
Each of the important Notes starts with Q, and we then want up to semi-colon.

Want to group using: FWP.category, new.code, BPS.rr
Hours are in FY.1.Hours
Eventually want to use Task...Name

```{r}
all.budget <- read_excel('../../MAGIS FY23 Budget for cuts v8.xlsx', sheet='Data Entry', skip=1)
names(all.budget) <- make.names(colnames(all.budget))
all.budget <- filter(all.budget, Employee.Name!='Na')
all.budget$new.code<-str_extract(all.budget$Notes,'^Q\\w+\\.\\w+')
all.budget$fiscal.year<-2023
all.budget$monthly.hours<-all.budget$FY.1.Hours/12
all.budget$Hours<-all.budget$FY.1.Hours
all.budget$Last.Name<-toupper(str_extract(all.budget$Employee.Name, '^\\w+'))
```


```{r}
bud.by.task <- group_by(all.budget,Task.Number, fiscal.year) %>% summarise(Hours=sum(Hours))
bud.by.code <- group_by(all.budget,new.code, fiscal.year) %>% summarise(Hours=sum(Hours))
bud.by.div <- group_by(all.budget,Division, fiscal.year) %>% summarise(Hours=sum(Hours))
bud.by.person <- group_by(all.budget,Employee.Name, fiscal.year) %>% summarise(Hours=sum(Hours))
bud.by.name <- group_by(all.budget,Last.Name, fiscal.year) %>% summarise(Hours=sum(Hours))
bud.by.cat <- group_by(all.budget,FWP.category, fiscal.year) %>% summarise(Hours=sum(Hours))

bud.by.div.person <- group_by(all.budget,Division, Employee.Name, fiscal.year) %>% summarise(Hours=sum(Hours))
bud.by.div.task <- group_by(all.budget,Division, Task.Number, fiscal.year) %>% summarise(Hours=sum(Hours))
bud.by.div.code <- group_by(all.budget,Division, new.code, fiscal.year) %>% summarise(Hours=sum(Hours))

```


unlist(as.POSIXlt(all.charges$Timecard.End[5001]))
sec   min  hour  mday   mon  year  wday  yday isdst 
  0     0     0    22     4   122     0   141     0 
  
What I really want are two new columns for each row: Year, Month
then group_by Task.Name, Year, Month, summarizing Hours

This is accumulated hours by task name and year.

```{r}
hours.by.task <- group_by(all.charges,Task.Name, fiscal.year, fiscal.month) %>% summarise(Hours=sum(Hours))
hours.by.task <- group_by(hours.by.task,Task.Name, fiscal.year) %>% mutate(cs=cumsum(Hours))

hours.by.cat <- group_by(all.charges,Function.Category,fiscal.year,fiscal.month)%>%summarise(Hours=sum(Hours)) 
hours.by.cat <- group_by(hours.by.cat,Function.Category, fiscal.year) %>% mutate(cs=cumsum(Hours)) 

hours.by.div <- group_by(all.charges,DSC, fiscal.year, fiscal.month) %>% summarise(Hours=sum(Hours))
hours.by.div <- group_by(hours.by.div,DSC, fiscal.year) %>% mutate(cs=cumsum(Hours))

hours.by.person <- group_by(all.charges,Last.Name,fiscal.year,fiscal.month)%>%summarise(Hours=sum(Hours)) 
hours.by.person <- group_by(hours.by.person,Last.Name, fiscal.year) %>% mutate(cs=cumsum(Hours)) 

hours.task.total <- group_by(all.charges,Task.Name,fiscal.year) %>% summarise(Hours=sum(Hours))
hours.cat.total <- group_by(all.charges,Function.Category,fiscal.year) %>% summarise(Hours=sum(Hours))
hours.person.total <- group_by(all.charges,Last.Name,fiscal.year) %>% summarise(Hours=sum(Hours))
hours.div.total <- group_by(all.charges,DSC,fiscal.year) %>% summarise(Hours=sum(Hours))
hours.div.task.total <- group_by(all.charges,DSC,Task.Name,fiscal.year) %>% summarise(Hours=sum(Hours))

```

```{r}
hours.task.plot <- ggplot(hours.by.task, aes(month,cs)) + geom_point()
hours.cat.plot <- ggplot(hours.by.cat, aes(month,cs)) + geom_point()

hours.task.plot <- hours.task.plot  + facet_grid(vars(Task.Name),vars(year))
hours.cat.plot <- hours.cat.plot  + facet_grid(vars(Function.Category),vars(year))
```


```{r}
print(hours.task.plot)
print(hours.cat.plot)
ggsave(hours.task.plot, filename="hoursbyyearbytask.pdf",units="in", height=10, device="pdf")
ggsave(hours.cat.plot, filename="hoursbyyearbyfunction.pdf",units="in", height=10, device="pdf")
```

```{r}
view(hours.task.total)
#print(hours.cat.total)
```

```{r}
datepart<-'Dec2022FY24Scenario'
datepart<-'Dec2022FY24ScenarioUpdated' # with delayed M&S
datepart<-'Dec2022FY23' # limited to 5.4M spending
datepart<-'Dec2022StatusInput'

read.my.file <- function(datepart, tab)
{
  fname<-paste('../extracted/tab_',tab,'_',datepart,'.csv',sep='')
  df <- read.csv(fname)
  df
}

taskrsrc<-read.my.file(datepart, 'TASKRSRC')
rsrc<-read.csv("../extracted/tab_RSRC_Dec2022FY24Scenario.csv")
wbs<-read.csv("../extracted/tab_PROJWBS_Dec2022FY24Scenario.csv")
tasks<-read.csv("../extracted/tab_TASK_Dec2022FY24Scenario.csv")
all.data<-read.csv("../output/alltasks.csv")
```

Sequence is 
Find line in TASKRSRC, first two columns are IDs: taskrsrc_id, task_id
Find task_id in TASK: there is a task ID and task name here, and task_id,proj_id,wbs_id.
Find wbs_id in PROJWBS: the name of this area is found here

```{r}
#view(all.data%>%select(name, wbs, category, group, wbs_high, wbs_low))

all.data<-filter(all.data, year(target_start)>2021)
all.data$g=as.numeric(as.factor(all.data$group))
gp<-ggplot(all.data, aes(xmin = as.Date(target_start), xmax = as.Date(target_end), 
                   y=group,# ymin = g, ymax = g+.8, 
                   fill = category)) +
  geom_rect(aes(ymin = g, ymax = g+.8)) +
  scale_y_discrete("group") +
  scale_x_date(date_breaks='1 month', date_labels = "%b %y") +
  theme(axis.text.x = element_text(angle = 90)) + 
  geom_text(aes(x = as.Date(target_start), label = wbs), nudge_x=39.6, nudge_y=.2, size=3)

ggsave(gp, filename="vs.pdf",units="in", height=10, width=24, device="pdf")
#print(gp)
```

```{r}
sched <- tasks %>% left_join(wbs, by=join_by(wbs_id)) %>% select( task_id, target_start_date, target_end_date, task_code, task_name, wbs_id, wbs_name, wbs_short_name) %>% arrange(target_start_date)
```


```{r}
costs <- filter(taskrsrc,target_cost>0) %>% left_join(tasks,by=join_by(task_id))%>%left_join(wbs, by=join_by(wbs_id)) %>% select( task_id, target_cost, cost_per_qty, target_start_date.x, target_end_date.x, task_code, task_name, wbs_id, wbs_name, wbs_short_name) %>% arrange(target_start_date.x)
view(costs)
```

Want to group using: FWP.category, new.code, BPS.rr
Hours are in FY.1.Hours

```{r}
div=filter(all.budget,Division=='AD')
select(div,FWP.category, FY.1.Hours) %>% group_by(FWP.category) %>% summarise(Hours = sum(FY.1.Hours))
select(div,new.code, FY.1.Hours) %>% group_by(new.code) %>% summarise(Hours =     sum(FY.1.Hours))
select(div,BPS.rr, FY.1.Hours) %>% group_by(BPS.rr) %>% summarise(Hours = sum(FY.1.Hours))
select(div,Task...Name, FY.1.Hours) %>% group_by(Task...Name) %>% summarise(Hours = sum(FY.1.Hours))
select(div,Employee.Name, FY.1.Hours) %>% group_by(Employee.Name) %>% summarise(Hours = sum(FY.1.Hours))
```


all.charges:   want column DSC=="AD"
```{r}

f<-FY(2023)
FY23.charges.AD <- filter(all.charges,DSC=="AD")
FY23.charges.AD <- filter(FY23.charges.AD, f(FY23.charges.AD))
FY23.task.total <- FY23.charges.AD %>% group_by(Task.Name) %>% summarise(Hours=sum(Hours))
FY23.cat.total <- FY23.charges.AD %>% group_by(Function.Category) %>% summarise(Hours=sum(Hours))
FY23.person.total <- FY23.charges.AD %>% group_by(Last.Name) %>% summarise(Hours=sum(Hours))
```



```{r}

person.bud <- filter(hours.by.person, fiscal.year==2023) %>% left_join(bud.by.name, by=join_by(Last.Name), suffix=c('.charges','.budget'))

tmp<-group_by(person.bud,Last.Name, fiscal.year.charges) %>% mutate(cs.bud=cumsum(Hours.budget/12))

hours.plot <- ggplot(tmp%>%filter(Last.Name=='KELLETT'), aes(fiscal.month)) + geom_point(aes(x=fiscal.month, y=cs)) + geom_point(aes(x=fiscal.month, y=cs.bud),colour='blue')
hours.plot <- hours.plot  + facet_grid(vars(Last.Name))
print(hours.plot)

```

