---
title: "R Notebook"
output: html_notebook
---


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(writexl)
library(stringr)
library(rlang)
library(lubridate)
library(scales)

library(MAGIS100PM)
```



```{r}
all <- get.all.schedule("WS2309")
all <- apply.baseline.schedule(all, "BCRBL2")
charges <- get.all.kronos()
people <- get.p6.people(charges, all)
tasks.people <- combine.tasks.people(people, all)
```

```{r}
labor <- bin.labor(tasks.people)
costs <- bin.expenses(all$all.data)
costs.week <- costs$target.by.week%>% filter(FY>=2023&FY<2028)%>%group_by(FY)%>%mutate(csum=cumsum(hsum))
```


Full.Name = Full.Name
Full.Name = Role

```{r}
kr.proc <- function(grouping.name, charges, st=as.Date("2023-03-01"), en=as.Date("2028-01-01"))
{
  grouping.sym = rlang::sym(grouping.name)

  # this is (a) the timeframe, (b) the fields renamed to common ones, (c) LOE clearly identified
  kr.tmp<- charges %>% filter(Timecard.Start>=st&Timecard.Start<=en) %>%
    select(FY=fiscal.year, d=Timecard.Start, Hours=Hours, Full.Name=Full.Name,ctc=taskcode,department=DSC, role=Role) %>%
    mutate(LOE=ctc=='Q1903.01') %>%
    mutate(role.new=if_else(LOE=='TRUE'&!is.na(ctc), "LOE", role))

  # this is a grouping by ctc, the parameter grouping name, and the week
  kr.tmp.1<- kr.tmp%>% group_by(ctc, !!grouping.sym, d) %>% summarise(sum=sum(Hours),.groups='keep')
  # this adds the cumulative total to the prior one
  kr.tmp.2<- kr.tmp.1%>% arrange(ctc, !!grouping.sym, d) %>% group_by(ctc, !!grouping.sym) %>% mutate(csum=cumsum(sum))
  # fix the grouping name to be the parameter string
  kr.tmp.1<- rename(kr.tmp.1, grouping=grouping.name)
  kr.tmp.2<- rename(kr.tmp.2, grouping=grouping.name)

  # produce the plots of hours per week and cumulative hours per week
  kr.tmp.g1<- ggplot(kr.tmp.1,aes(x=d, y=sum)) + geom_step() + facet_wrap(vars(ctc,grouping),scales="free_y")
  kr.tmp.g2<- ggplot(kr.tmp.2,aes(x=d, y=csum)) + geom_step() + facet_wrap(vars(ctc,grouping),scales="free_y")

  # return everything (charges with all fields, hours by ctc and arg, cumu hours by ctc and group)
  list(kr=kr.tmp, kr1=kr.tmp.1, kr2=kr.tmp.2, kr.g1=kr.tmp.g1, kr.g2=kr.tmp.g2)
}

p6.proc <- function(grouping.name, labor.by.week, st=as.Date("2023-03-01"), en=as.Date("2024-03-01"))
{
  grouping.sym = rlang::sym(grouping.name)
  
  # this is (a) the timeframe, (b) the fields renamed to common ones, (c) LOE clearly identified
  p6.tmp<- labor.by.week %>% filter(week>=st&week<=en) %>%
    select(FY=FY, d=week, Hours=dl.hours, Full.Name=person, department=code, ctc=ctc, role=Role) %>%
    mutate(LOE=ctc=='Q1903.01')%>%
    mutate(role.new=if_else(LOE=='TRUE'&role!="RA", "LOE", role))

  # this is the same as the kr code
  p6.tmp.1<- p6.tmp %>% group_by(ctc, !!grouping.sym, d) %>% summarise(sum=sum(Hours),.groups='keep')
  p6.tmp.2<- p6.tmp.1%>% arrange(ctc, !!grouping.sym, d) %>% group_by(ctc, !!grouping.sym) %>% mutate(csum=cumsum(sum))
  p6.tmp.1<- rename(p6.tmp.1, grouping=grouping.name)
  p6.tmp.2<- rename(p6.tmp.2, grouping=grouping.name)

  p6.tmp.g1<- ggplot(p6.tmp.1,aes(x=d, y=sum)) + geom_step() + facet_wrap(vars(ctc,grouping),scales="free_y")
  p6.tmp.g2<- ggplot(p6.tmp.2,aes(x=d, y=csum)) + geom_step() + facet_wrap(vars(ctc,grouping),scales="free_y")
  
  list(p6=p6.tmp, p61=p6.tmp.1, p62=p6.tmp.2, p6.g1=p6.tmp.g1, p6.g2=p6.tmp.g2)
}

```

Full.Name = person
Full.Name = Role

labor$by.week.person
labor$by.week.role


```{r}

#kr.data <- kr.proc("role.new", charges%>%filter(taskname=="Q1903.10"))
kr.data <- kr.proc("role.new", charges)
p6.data <- p6.proc("role.new", labor$by.week.ctc) # role
```


#```{r}
print(kr.data$kr.g1)
print(kr.data$kr.g2)

ggsave(kr.data$kr.g1, filename=paste(base.path,"/HoursByName.pdf",sep=''),units="in", height=12, width=24, device="pdf")
ggsave(kr.data$kr.g2, filename=paste(base.path,"/CumuHoursByName.pdf",sep=''),units="in", height=12, width=24, device="pdf")
# ```

#```{r}
print(p6.data$p6.g1)
print(p6.data$p6.g2)

ggsave(p6.data$p6.g1, filename=paste(base.path,"/P6HoursByName.pdf",sep=''),units="in", height=12, width=24, device="pdf")
ggsave(p6.data$p6.g2, filename=paste(base.path,"/P6CumuHoursByName.pdf",sep=''),units="in", height=12, width=24, device="pdf")

#```

```{r}
#person.diff <- setdiff(unique(charges$Full.Name), unique(labor$by.week.person$person))
person.comp <- rbind(mutate(p6.data$p62,from="P6"),mutate(kr.data$kr2,from="KR"))
  #left_join(mutate(tmp.2,from="KR"), by=join_by(Full.Name,d), suffix=c(".p6",".kr"))
```

# mutate(d=ceiling_date(d, unit="month"))%>%
# group_by(FY,from, ctc,week)%>%summarise(sum=sum(sum), csum=sum(csum))

#person.comp.p <- pivot_wider(person.comp, names_from=c("from"), values_from = c("sum","csum"))
#person.comp.p <- full_join(person.comp%>%filter(from=="KR"),person.comp%>%filter(from=="P6"), by=join_by(d,ctc,grouping), 

person.comp.p <- person.comp %>% filter(d<as.Date("2023-10-01")) %>% 
  group_by(from,d,grouping) %>% summarise(sum=sum(sum), csum=sum(csum))
person.comp.p <- full_join(person.comp.p%>%filter(from=="KR"),person.comp.p%>%filter(from=="P6"), by=join_by(d,grouping), suffix=c(".KR",".P6")) %>% 
  mutate(sum.KR=replace_na(sum.KR,0), sum.P6=replace_na(sum.P6,0)) %>%
  mutate(csum.KR=replace_na(csum.KR,0), csum.P6=replace_na(csum.P6,0))

person.g3p<- ggplot(person.comp.p,aes(x=d)) + 
  geom_step(aes(y=csum.KR, colour=from.KR)) +
  geom_step(aes(y=csum.P6, colour=from.P6)) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y") +
  facet_wrap(vars(grouping),scales="free_y") + 
  #facet_wrap(vars(ctc,grouping),scales="free_y") + 
  theme(axis.text.x = element_text(angle = 90))
person.g3pb<- ggplot(person.comp.p,aes(x=d, y=(csum.KR-csum.P6))) + 
  geom_step() +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y") +
  facet_wrap(vars(grouping),scales="free_y") + 
  #facet_wrap(vars(ctc,grouping),scales="free_y") + 
  theme(axis.text.x = element_text(angle = 90))

print(person.g3p)
print(person.g3pb)


person.g3<- ggplot(person.comp,aes(x=d, colour=from)) + 
  geom_step(aes(y=csum)) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y") +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(vars(ctc,grouping),scales="free_y")

print(person.g3)
ggsave(person.g3, filename=paste(base.path,"output/CumuHoursByRole.pdf",sep=''),units="in", height=12, width=24, device="pdf")

```{r}
tmp<- person.comp %>% ungroup() %>% select(from, d, isum=sum) %>% group_by(from,d)%>% summarise(sum=sum(isum)) %>% arrange(from, d) %>% group_by(from) %>% mutate(csum=cumsum(sum))

tmp2<- person.comp %>% ungroup() %>% filter(ctc!="Q1903.01" & d>=as.Date("2023-10-01")) %>% select(from, d, isum=sum) %>% group_by(from,d)%>% summarise(sum=sum(isum)) %>% arrange(from, d) %>% group_by(from) %>% mutate(csum=cumsum(sum))

# p6.data$p6 %>% mutate(Full.Name=if_else(is.na(Full.Name),role.new,Full.Name)) %>% distinct(Full.Name) %>% view()
# mutate(Full.Name=toupper(str_split_i(Name,", ",i=1)))

hours.per.person.per.week <- p6.data$p6 %>% filter(d>=as.Date("2023-10-01")) %>% ungroup() %>%
  mutate(Full.Name=if_else(is.na(Full.Name),role.new,Full.Name)) %>%
  mutate(Last.Name=toupper(str_split_i(Full.Name,", ",i=1))) %>%
  select(week=d, Last.Name, ctc, hours=Hours) %>%
  group_by(Last.Name, week) %>% summarize(hours=sum(hours)) %>% ungroup() %>%
  arrange(Last.Name, week) %>% group_by(Last.Name) %>% mutate(chours=cumsum(hours))
```


```{r}
person.g4<- ggplot(tmp2,aes(x=d, colour=from)) + 
  geom_line(aes(y=csum)) +
  scale_color_hue(labels = c("Kronos", "P6")) +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(name="cumulative hours",n.breaks=6) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y")

#  geom_step(aes(y=csum)) +
#  facet_wrap(vars(from),scales="free_y")
print(person.g4)
```

```{r}
ctc.comp <- rbind(mutate(p6.data$p6,from="P6"),mutate(kr.data$kr,from="KR"))

tmp<- ctc.comp %>% ungroup() %>% select(from, FY, ctc, d, Hours) %>% group_by(FY,from,ctc,d)%>% summarise(sum=sum(Hours)) %>% arrange(FY, from, ctc, d) %>% group_by(FY, from, ctc) %>% mutate(csum=cumsum(sum))
```

ctc.g5b<- ggplot(tmp%>%filter(FY==2023)%>% mutate(week=ceiling_date(d, unit="month"))%>%group_by(FY,from, ctc,week)%>%summarise(tot=sum(sum)),
                 aes(x=week, colour=from)) + 
  geom_line(aes(y=tot)) +
#  geom_step(aes(y=csum)) +
  facet_wrap(vars(FY,ctc),scales="free_y", nrow=1) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y") +
  #scale_y_continuous(name="cumulative costs", n.breaks=6) +
        theme(axis.text.x = element_text(angle = 90))
print(ctc.g5b)



ctc.g5<- ggplot(tmp,aes(x=d, colour=from)) + 
  geom_step(aes(y=csum)) +
#  geom_step(aes(y=csum)) +
  facet_wrap(vars(FY,ctc),scales="free_y")
print(ctc.g5)

#```{r}
tmp2<- ctc.comp %>% ungroup() %>% select(from, FY, name=role.new, d, Hours) %>% group_by(FY,from,name,d)%>% summarise(sum=sum(Hours)) %>% arrange(FY, from, name, d) %>% group_by(FY, from, name) %>% mutate(csum=cumsum(sum))
#```

person.g6<- ggplot(tmp2,aes(x=d, colour=from)) + 
  geom_line(aes(y=csum)) +
#  geom_step(aes(y=csum)) +
  facet_wrap(vars(FY,name),scales="free_y")
print(person.g6)
#```

```{r}
tmp2<- ctc.comp %>% ungroup() %>% 
  select(from, FY, ctc, d, Hours) %>% 
  filter(FY%in%c(2023,2024)& !is.na(ctc)) %>%
  arrange(from, FY, ctc, d) %>% 
  group_by(from,ctc,d)%>%
  summarise(sum=sum(Hours)) %>%
  ungroup() %>% 
  group_by(from, ctc) %>% 
  mutate(csum=cumsum(sum)) %>%
  mutate(week=ceiling_date(d, unit="month"))

tmp2b<- tmp2%>%
  arrange(from,ctc,week) %>% 
  group_by(from, ctc, .drop=FALSE)%>%
  mutate(tot=cumsum(sum))

ctc.g5c<- ggplot(tmp2b,
                 aes(x=d, colour=from)) + 
  geom_line(aes(y=tot)) +
  #geom_step(aes(y=csum)) +
  facet_wrap(vars(ctc),scales="free_y", nrow=1) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y") +
  scale_y_continuous(name="cumulative hours", n.breaks=6) +
        theme(axis.text.x = element_text(angle = 90))
print(ctc.g5c)

ctc.g5z<- ggplot(tmp2b %>% group_by(from, ctc, week) %>% summarize(ssum=sum(sum)),
                 aes(x=week, colour=from)) + 
  geom_line(aes(y=ssum)) +
  #geom_step(aes(y=csum)) +
  facet_wrap(vars(ctc),scales="free_y", nrow=1) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y") +
  scale_y_continuous(name="cumulative hours", n.breaks=6) +
        theme(axis.text.x = element_text(angle = 90))
print(ctc.g5z)


```

```{r}

#kr <- kr.proc("role.new", charges, en=as.Date("2028-01-01"))
p6 <- p6.proc("role.new", labor$by.week.ctc, en=as.Date("2028-01-01")) # role

monthly <- p6$p6 %>% select(d, Hours) %>% mutate(week=ceiling_date(d, unit="month")) %>%
  arrange(week) %>% group_by(week) %>% summarise(tot=sum(Hours)) %>% mutate(ctot=cumsum(tot))

g5d<- ggplot(monthly,
                 aes(x=week)) + 
  #geom_step(aes(y=tot)) +
  geom_line(aes(y=ctot)) +
    scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y") +
  scale_y_continuous(name="cumulative hours", n.breaks=6) +
        theme(axis.text.x = element_text(angle = 90))
print(g5d)

```



```{r}
k<- kr.proc("Full.Name", charges)
dist.ctc<- k$kr2 %>% ungroup() %>% filter(!is.na(ctc)) %>% select(ctc) %>% distinct(ctc) %>% pull()

plot.ctc <- function(ctcin)
{
  print(ctcin)
  dset<- k$kr2
  
  tmpp<- ggplot(dset%>%filter(ctc==ctcin), aes(x=d, y=csum)) + 
    geom_line() + 
    facet_wrap(vars(grouping), scales="free", ncol=5)
  print(tmpp)
  tmpp
}

#tmpp<- plot.ctc('Q1903.01')
vplot.ctc<- Vectorize(plot.ctc)
vplots <- vplot.ctc(dist.ctc)

#ggsave("../output/kr2_cyc.pdf", tmpp)
#print(tmpp)
```


```{r}

```

