---
title: "R Notebook"
output: html_notebook
---


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(writexl)
library(stringr)
library(rlang)
library(lubridate)
library(scales)

library(MAGIS100PM)
```



```{r}
all <- get.all.schedule("WS2408")
all <- apply.baseline.schedule(all, "BL2408BCR010")
#all$all.data <- all$all.data %>% filter(area==11)
charges <- get.all.kronos()
people <- get.p6.people(charges, all)
tasks.people <- combine.tasks.people(people, all)
```

```{r}
labor <- bin.labor(tasks.people)
costs <- bin.expenses(all$all.data)
costs.week <- costs$target.by.week%>% filter(FY>=2023&FY<2028)%>%group_by(FY)%>%mutate(csum=cumsum(hsum))
```





Name $ Actuals+March23 $ FY23 Q3-4 $ FY24 $ FY25 $ FY26 $ FY27 $ Totals
Planned work $ 3,913,740 $ 2,146,677 $ 1,768,276 $ 3,073,656 $ 3,317,993 $ 1,495,395 $ 15,715,738
Guidance $ 5,400,000 $ 1,000,000 $ 2,000,000 $ 4,000,000 $ 4,000,000 $ 3,331,336 $ 19,731,336

carryover  $5,018,000 $ 0		 $3,382,000 	 $4,000,000 	 $4,000,000 	 $3,295,832 

2/27/2023: BCWS=3,611,484	BCWP=3,611,484	ACWP=3,611,484

          BCWS      BCWP      ACWP      BAC         EAC
6/30/2023 4,671,765	4,223,610	4,273,491 15,714,400	15,727,715
9/30/2023 5,415,397	4,785,084	4,948,566 15,752,059	15,758,634




```{r}
d.laser.atom.interactions <- as.Date("2027-04-02")
#d.last.reporting.date <- as.Date("2023-09-30")
#d.last.reporting.date <- as.Date("2023-12-31")
d.last.reporting.date <- as.Date("2024-06-30")
d.now = as.Date(now())

pmp <- data.frame(
  names=c("Actuals+March23","FY23 Q3-4", "FY24", "FY25", "FY26", "project end", "FY27")
  ,dates=c("2023-04-01", "2023-10-01", "2024-10-01", "2025-09-30", "2026-09-30", "2027-04-02", "2027-09-30")
  ,planned=c(3913740,2146677,1768276,3073656,3317993,1495395,0)
  ,guidance=c(5400000,1000000,2000000,4000000,4000000,3331336,0)
  ,planned.carryover=c(3899212,1488355,2283370, 3274925, 3310015, 1495395,0)
  ,guidance.carryover=c(3899212,1488355,3382000-369567, 4000000,4000000, 3295832,0)
  ) %>% 
  mutate(
    cumu.planned=cumsum(planned)
    ,cumu.guidance=cumsum(guidance)
    ,cumu.planned.co=cumsum(planned.carryover)
    ,cumu.guidance.co=cumsum(guidance.carryover)
    ,dates=ymd(dates)
    ,timestamps=as.numeric(as_datetime(dates))
  )

min.planned <- first(pmp$planned)
max.planned <- max(pmp$planned)

fyears <- data.frame(
  names=c("FY24", "FY25", "FY26", "FY27", "Last Status", "Now", "Project End" ),
  dates=c( as.Date("2023-10-01"), as.Date("2024-10-01"), as.Date("2025-10-01"), as.Date("2026-10-01"),d.last.reporting.date, d.now, d.laser.atom.interactions),
  colors=c("yellow","yellow","yellow","yellow","lightblue","lightblue","lightblue"),
  alphas=c(1.0,1.0,1.0,.4,.4,.4,.4),
  ypos=c(min.planned, min.planned, min.planned, min.planned,max.planned+1e6, 8e6, min.planned+1e6)
)

max.dates <- max(fyears$dates)
min.dates <- min(fyears$dates)

fcosts <- data.frame(
  colors=c("grey70","grey70","grey75","grey75","grey75","grey75",
           "grey80","grey80","grey90","grey90","grey90","grey90"),
  costs=c(15715738.00, 19731336.00, 16279373, 17203460, 16771287, 16150319, 
          16052283,15691757, 15915541,15752059, 15764280,15714400),
  names=c("PMP Planned Work", "PMP Guidance", "EAC Jun24", "BAC Jun24", "EAC Mar24", "BAC Mar24", 
          "EAC Dec23", "BAC Dec23", "EAC Sep23", "BAC Sep23", "EAC Jun23", "BAC Jun23"),
  xpos=c(min.dates, min.dates, max.dates, max.dates, max.dates, max.dates, 
         max.dates, max.dates, max.dates, max.dates, max.dates, max.dates)
)

fcprs <- read_xlsx("../../Finance/SummaryCPRs.xlsx")
fcprs <- fcprs %>% filter(str_detect(Name,"Totals")) %>% arrange(End.Date)
fcprs <- fcprs %>% mutate(Period=as.Date(Period), Completion.Date=as.Date(Completion.Date))
fcprs.p <- pivot_longer(fcprs, c("BCWS", "BCWP", "ACWP", "BAC", "EAC"))


#print(ggplot(pmp, aes(x=timestamps, y=cumu.guidance)) + geom_line())

```

Work Scheduled = BCWS = Budgeted cost of work scheduled	
Work Performed = BCWP = Budgeted cost of work performed	
Actual Cost    = ACWP = Actual cost of work performed
SV = schedule variance


What's left?  
Need table of CPR data, with dates of measurement and completion dates for that schedule.
There should be a starting record at 3/1/2023 (This is the line from Jan-23 entry with 3611484 BCWS)
There should be two records with BAC/EAC filled in (Jun, Sept).
There could be one more with BCWP, BCWS, ACWP filled in from April.

columns: cpr.date, BCWS, BCWP, ACWP, SW, CV, BAC, EAC, completion.date

"2023-03-01", 3611484,	3611484,	3611484,	0,        0,      NA, NA, "2027-04-02"
"2023-04-30", 4059270,	3896789,	3911762,	-162481, -14,973, NA, NA, "2027-04-02"
"2023-06-30", 4671765,	4223610,	4273491,	-448155, -49,881, 15714400,	15727715, "2027-04-02"
"2023-09-30", 5415397,	4785084,	4948566,	-630312, -163,482,15752059,	15758634, "2027-04-02"


Attention:
Show probably add a third line that is the current baseline.  
Other is really the PMP schedule (BL2307)

```{r}
baseline.current <- get.all.schedule("BL2408BCR010")
#baseline.current <- get.all.schedule("WS2312")
#baseline.current$all.data <- baseline.current$all.data %>% filter(area==11)

baseline.current.costs <- bin.expenses(baseline.current$all.data)
baseline.pmp <- get.all.schedule("BL2307")
baseline.pmp.costs <- bin.expenses(baseline.pmp$all.data)

# JBK - adjusting to use ACWP as starting point for forecast
# replace ctot for first prerollup==TRUE with latest ACWP
# mutate(ctot = replace(ctot, ctot==old.start, new.acwp))
latest.ACWP <- fcprs %>% slice_max(Period) %>% pull(ACWP)

WS.monthly <- costs$target.by.month  %>% 
  arrange(week) %>% group_by(week) %>% summarise(tot=sum(hsum)) %>%
  mutate(ctot=cumsum(tot)) %>%
  #mutate(prerollup=week<as.Date("2023-03-03"), from="2403.Forecast") 
  mutate(prerollup=week<d.last.reporting.date, from="2406.Forecast") %>%
  filter(prerollup==FALSE)

first.month.tot <- WS.monthly %>% slice_head() %>% pull(tot)

# JBK - this is a bit sloppy - we will start at d.last.reporting.date with
# the ACWP from the last period.
WS.monthly <- WS.monthly %>% 
  add_row(week=floor_date(d.last.reporting.date,unit="month"),
          tot=latest.ACWP-first.month.tot,ctot=latest.ACWP-first.month.tot,
          prerollup=TRUE,from="2406.Forecast" ,.before=1) %>%
  mutate(ctot=cumsum(tot))



BL.monthly <- baseline.current.costs$target.by.month  %>% 
  arrange(week) %>% group_by(week) %>% summarise(tot=sum(hsum)) %>%
  mutate(ctot=cumsum(tot)) %>%
  mutate(prerollup=week<as.Date("2023-03-03"), from="2406.Baseline") 

PMP.monthly <- baseline.pmp.costs$target.by.month  %>% 
  arrange(week) %>% group_by(week) %>% summarise(tot=sum(hsum)) %>%
  mutate(ctot=cumsum(tot)) %>%
  mutate(prerollup=week<as.Date("2023-03-03"), from="2307.PMP") 

monthly=rbind(WS.monthly, BL.monthly, PMP.monthly)
```

```{r}
# need to use the ggplot function definition functions for this,
# that is: ggptoto() and layer()
# https://ggplot2.tidyverse.org/articles/extending-ggplot2.html 
vline_labeled <- function(value, label="", col="black", alpha=1.0, ...)
{
  geom_vline(aes(xintercept=value),alpha=alpha, colour=col, ...)+
    geom_text(aes(x = value, label = label, hjust="left",vjust="bottom"))
}

gen.evms <- function(filt.date, filt.cost)
{

filt.data <- list(
  months = monthly %>% filter(prerollup==FALSE & week<filt.date),
  pmp = pmp %>% filter( dates<filt.date),
  fyears = fyears %>% filter( dates<filt.date),
  fcprs = fcprs.p %>% filter( Period<filt.date & Period>=as.Date("2023-01-01")),
  fcosts = fcosts %>% filter( xpos<filt.date & costs<filt.cost)
)

g5d<- ggplot(filt.data$months,
                 aes(x=week, colour=from)) + 
  
  geom_ribbon(data=filt.data$pmp, aes(x=dates,ymin=cumu.planned, ymax=cumu.guidance),
              inherit.aes=FALSE, fill="lightyellow",alpha=.6) +
  geom_ribbon(data=filt.data$pmp, aes(x=dates,ymin=cumu.planned.co, ymax=cumu.guidance.co),
              inherit.aes=FALSE, fill="orange",alpha=.2) +
  
  geom_vline(data=filt.data$fyears, aes(xintercept=dates), alpha=1.0, colour=filt.data$fyears$colors) +
  geom_text(data=filt.data$fyears, aes(x=dates,y=ypos, label=names, hjust="left",vjust="top"),
            size=3,inherit.aes=FALSE, check_overlap = TRUE, nudge_y=-1e5) +
  # width=8.0
  
  geom_hline(data=filt.data$fcosts, aes(yintercept=costs), colour=filt.data$fcosts$colors)+
  geom_text(data=filt.data$fcosts, aes(y=costs,x=xpos, label=names, hjust="left",vjust="bottom"),
            size=2.5,inherit.aes=FALSE, check_overlap = TRUE, nudge_y=1e5) +

  geom_point(data=filt.data$fcprs%>%filter(!str_detect(name,"BAC|EAC")), aes(x=Period, y=value, colour=name), inherit.aes = FALSE, show.legend = TRUE) + 
  geom_line(data=filt.data$fcprs%>%filter(!str_detect(name,"BAC|EAC")), aes(x=Period, y=value, colour=name), inherit.aes = FALSE, show.legend = FALSE) + 
  #geom_jitter(data=fcprs.p%>%filter(str_detect(name,"BAC|EAC")), aes(x=Completion.Date, y=value, colour=name), inherit.aes = FALSE) + 

  geom_line(aes(y=ctot)) +
  
  #scale_color_hue(labels = c("A","B","C","PMP schedule", "Baseline 2023-09")) +
  scale_x_date(name="Date (by month)", date_breaks='2 month', date_labels = "%b %y") +
  scale_y_continuous(name="cumulative expenses", n.breaks=10, 
                     labels=label_number(scale=1e-6,accuracy=.1,prefix="$", suffix="M")) +
  theme(axis.text.x = element_text(angle = 90))
g5d
}
```

```{r}

filt.date <- as.Date("2028-10-02")
filt.cost <- 30e6

evms.full<- gen.evms(as.Date("2028-10-02"), 30e6)
evms.zoom<- gen.evms(as.Date("2024-10-02"), 10e6)

print(evms.full)
print(evms.zoom)
# width=12, height=10,
ggsave(evms.zoom, filename=paste(base.path,"/output/evms_zoom.pdf",sep=''), units="in", device="pdf")
ggsave(evms.full, filename=paste(base.path,"/output/evms_full.pdf",sep=''), units="in", device="pdf")

# shows guidance envelope
```

Additional steps for ETC analysis of WBS Infrastructure (11)

```{r}

area11BL<-baseline.current$all.data %>% filter(area==11) %>% select(code, name, cost, total_cost, rsrc_type, total_float, target_start,status)

area11WS <- all$all.data %>% filter(area==11) %>% select(code, name, wbs, wbs_low, cost, total_cost, rsrc_type, total_float, target_start,target_end, baseline_start, baseline_end, status) %>% arrange(wbs, cost)

area11BL %>% view("BL")
area11WS %>% view("WS")

area11WS %>% summarise(ts=sum(total_cost, na.rm=TRUE))
area11BL %>% summarise(ts=sum(total_cost, na.rm=TRUE))

area11WS %>% group_by(wbs_low, status, rsrc_type) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType")
area11WS %>% group_by(status, wbs_low) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.stat.wbs")
area11WS %>% group_by(status, rsrc_type) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.stat.rsrc")
area11WS %>% group_by(wbs_low) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.wbs")
area11WS %>% group_by(status) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.stat")
area11WS %>% group_by(rsrc_type) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.rsrc")

area11WS %>% filter(wbs=="11.07") %>% arrange(desc(total_cost)) %>% view("WSbyEE")

```
 

Additional steps for ETC analysis of WBS Infrastructure (12)

```{r}

area12BL<-baseline.current$all.data %>% filter(area==12) %>% select(code, name, cost, total_cost, rsrc_type, total_float, target_start,status)

area12WS <- all$all.data %>% filter(area==12) %>% select(code, name, wbs, wbs_low, cost, total_cost, rsrc_type, total_float, target_start,target_end, baseline_start, baseline_end, status) %>% arrange(wbs, cost)

area12BL %>% view("BL")
area12WS %>% view("WS")

area12WS %>% summarise(ts=sum(total_cost, na.rm=TRUE))
area12BL %>% summarise(ts=sum(total_cost, na.rm=TRUE))

area12WS %>% group_by(status, wbs_low) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.stat.wbs")
area12WS %>% group_by(status, rsrc_type) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.stat.rsrc")
area12WS %>% group_by(wbs_low) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.wbs")
area12WS %>% group_by(status) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.stat")
area12WS %>% group_by(rsrc_type) %>% summarise(ts=sum(total_cost, na.rm=TRUE)) %>% view("WSbyType.rsrc")

#area12WS %>% filter(wbs=="11.07") %>% arrange(desc(total_cost)) %>% view("WSbyEE")

```


Cumulative costs by CTC (this is ETC summary numbers)
```{r}
#jbk.ctc.mins <- group_by(costs$target.by.month.ctc, ctc)%>% slice_min(hsum, with_ties=FALSE)

jbk.WS.monthly <- costs$target.by.month.ctc %>% ungroup() %>% filter(week>as.Date("2024-06-30")) %>% 
    arrange(ctc,week) %>% group_by(ctc,week) %>% summarise(tot=sum(hsum)) %>%
    mutate(ctot=cumsum(tot)) %>%
    #mutate(prerollup=week<as.Date("2023-03-03"), from="2403.Forecast") 
    mutate(prerollup=week<d.last.reporting.date, from="2406.Forecast") %>%
    filter(prerollup==FALSE)
jbk.months<- jbk.WS.monthly %>% filter(prerollup==FALSE & week<as.Date("2027-10-02"))

print(ggplot(jbk.months, aes(x=week, colour=ctc)) + geom_line(aes(y=ctot)))

```

