---
title: "Labor Tracking Tool"
output: html_notebook
---

```{r message=FALSE, warning=TRUE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(writexl)
library(stringr)
library(lubridate)
library(RColorBrewer)

library(MAGIS100PM)
```

```{r}
sched.name <- "WS2503"
sched.base <- "BL2412"

all <- get.all.schedule(sched.name) 
all <- apply.baseline.schedule(all, sched.base)
charges <- get.all.kronos()

# test cleanup of charges, what distinct rows of Fermi.ID, Transaction.Date, Charge.Task.Code
# distinct(Fermi.ID, Transaction.Date, Charge.Task.Code, .keep_all=TRUE) %>% 
# this distinct thing is now in the library function get.all.kronos 

people <- get.p6.people(charges, all)
tasks.people <- combine.tasks.people(people, all)

labor <- bin.labor(tasks.people)
costs <- bin.expenses(all$all.data)
```

```{r}
months.forward <- 3
months.back <- 2
filt.st<-as.Date(now())
filt.ws<-as.Date("2025-03-31")
filt.en<-filt.st + months(months.forward)
filt.bk<-as.Date("2025-03-05")  # filt.st - months(months.back)
filt.name<- paste("LaborTracking",month(filt.st, label=TRUE, abbr=FALSE))
filt.asof<- filt.st

ending <- paste("_LaborTracking",filt.st,"_",filt.en,".xlsx",sep='')
```

This pull all the records that fall in our range using the expect

```{r message=FALSE, warning=FALSE}
#| echo: false

p6.hours<- labor$by.week.all %>% ungroup() %>% 
  filter(week>=filt.bk & week<=filt.en) %>%
  select(task_id, week, hours=dl.hours, Full.Name=person, department=code, ctc=ctc, role=Role) %>%
  mutate(LOE=ctc=='Q1903.01')%>%
  mutate(role.new=if_else(LOE=='TRUE'&role!="RA", "LOE", role)) %>%
  mutate(Full.Name=if_else(is.na(Full.Name),role.new,Full.Name)) %>%
  mutate(Last.Name=toupper(str_split_i(Full.Name,", ",i=1))) %>% 
  #select(-Full.Name) %>%
  mutate(period=if_else(week<filt.st, "before","after"))

p6.hours.sum <- p6.hours %>% 
  select(period, person=Full.Name, task_id, ctc, hours) %>% 
  group_by(period, person, task_id, ctc) %>% 
  summarise(total_hours=sum(hours)) %>%
  arrange(person) %>% 
  pivot_wider(names_from=period, values_from=total_hours)
```

```{r}
kr.hours<- charges %>% 
  filter(Timecard.Start>=filt.bk & Timecard.Start<filt.en) %>%
  select(Full.Name, Last.Name, week=Timecard.Start, hours=Hours, ctc=taskcode, department=DSC, role=Role) %>%
  mutate(LOE=ctc=='Q1903.01') %>%
  mutate(role.new=if_else(LOE=='TRUE'&!is.na(ctc), "LOE", role)) %>%
  mutate(period=if_else(week<filt.st, "PastHoursCharged","HoursChargedAfterReportDate"))

kr.hours.sum <- kr.hours %>% 
  select(period, person=Full.Name, TaskCode=ctc, hours) %>% 
  group_by(period, person, TaskCode) %>% 
  summarise(HoursCharged=sum(hours)) %>%
  mutate(HoursCharged=as.integer(HoursCharged)) %>%
  arrange(person,TaskCode) %>% 
  pivot_wider(names_from=period, values_from=HoursCharged) 
#%>%
#  view()


person.comp <- bind_rows(p6=p6.hours, kronos=kr.hours, .id="src")

```

The task records we are interested in

```{r}

int.future <- interval(filt.st, filt.en)
int.past <- interval(filt.bk, filt.st)

p6.rsrc <- tasks.people %>%
  #filter(target_start_date<=filt.en & target_end_date>=filt.bk) %>% 
  filter(start<=filt.en & finish>=filt.bk) %>% 
  select(task_id, target_start_date, target_end_date, target_qty, role_name, rsrc_name)

p6.tasks <- all$all.data %>% 
  filter(start<=filt.en & finish>=filt.bk) %>% 
  select(task_id,ctc, wbs, code, name, start, finish, status,dur)

p6.recs <- p6.tasks %>% 
  left_join(p6.rsrc, by=join_by(task_id)) %>% 
  filter(ctc!="Q1903.01" | is.na(ctc)) %>% 
  mutate(kind=if_else(str_detect(name,"M&S"),"4-M&S",
                      if_else(str_detect(name,"Milestone"),"3-Milestone",
                              if_else(str_detect(wbs,"00."),"5-In_Kind","1-Normal")))) %>%
  mutate(person=if_else(kind=="1-Normal",role_name, substr(kind,3,20))) %>%
  mutate(kind=if_else(is.na(person), "2-Title", kind)) %>%
  mutate(person=if_else(is.na(person),rsrc_name, person)) %>%
  mutate(status = case_when(status=="TK_NotStart" ~ "Not Started", 
                           status=="TK_Active" ~ "Active",
                           status=="TK_Complete" ~ "Complete",
                           TRUE ~ "Unknown")) %>% 
  left_join(p6.hours.sum, by=join_by(person, task_id, ctc)) %>% 
  select(Person=person, TaskDescription=name, TaskCode=ctc, WBS=wbs, 
         Activity=code, WorkingSchedStart=start, WorkingSchedEnd=finish,
         ScheduledHours=target_qty, Status=status, kind, 
         HoursBefore=before, HoursAfter=after) %>%
  mutate(TotalScheduledHours=as.integer(ScheduledHours),
         ScheduledHoursUpcoming=as.integer(HoursAfter),
         ScheduledHoursToDate=as.integer(HoursBefore)) %>%
  arrange(kind, Person, WBS, WorkingSchedStart) %>%
  #select(-kind, -Status, -HoursBefore,-HoursAfter,-ScheduledHours) %>% 
  select(-kind, -HoursBefore,-HoursAfter,-ScheduledHours) %>% 
  mutate(KronosHours=NA, EstimatedFinishDate=NA,notes='') 
#%>% 
#  view()

```

```{r}
p6.reviews <- all$all.data %>% 
  filter(start<=filt.en & finish>=filt.bk) %>% 
  select(Activity=code, Description=name,TaskCode=ctc, WBS=wbs,
         WorkingSchedStart=start, WorkingSchedEnd=finish, 
         status) %>%
  filter(str_detect(Description,"[Rr]eview")) %>%
  mutate(status = case_when(status=="TK_NotStart" ~ "Not Started", 
                           status=="TK_Active" ~ "Active",
                           status=="TK_Complete" ~ "Complete",
                           TRUE ~ "Unknown")) %>% 
  mutate(kind = case_when(str_detect(Description,"[Ff]inal") ~ "Final", 
                          str_detect(Description,"[Pp]reliminary") ~ "Preliminary",
                          TRUE ~ "Unknown")) %>% 
  arrange(WorkingSchedStart)
#%>%
#  view()

```

Add title tab with Report Date (filt.st), past date (filt.bk), future date(filt.en)

Total Scheduled Hours = Hours for entire duration of task
Scheduled Hours Upcoming = Hours scheduled for next 3 months
Scheduled Hours to Date = Calculated hours that should have been used by the report date.  Ideally these will match Kronos Hours, and differences are useful to know.
Kronos Hours = People are asked to assign hours to each task from the total listed on “Charges” tab
Estimated Finish = Provide update if end date listed is not realistic.
Notes = Let us know how we can help.  Examples include missing resources or requirements, or suggested BCR, or needs attention in any way.

```{r}

report.title <- data.frame(Name=c('ReportDate', 'PastDate', 'FutureDate', 'WorkingScheduleDate',
                                  'Total Scheduled Hours', 
                                  'Scheduled Hours Upcoming', 
                                  'Scheduled Hours to Date',
                                  'Kronos Hours', 
                                  'Estimated Finish', 
                                  'Notes'),
                           Value=c(as.character(filt.st), as.character(filt.bk), as.character(filt.en), as.character(filt.ws),
                                   'Hours for entire duration of task',
                                   paste('Hours scheduled for next',months.forward,'months'),
                                   'Calculated hours that should have been used by the report date.  Ideally these will match Kronos Hours, and differences are useful to know',
                                   'People are asked to assign hours to each task from the total listed on “Charges” tab',
                                   'Provide update if end date listed is not realistic',
                                   'Let us know how we can help.  Examples include missing resources or requirements, or suggested BCR, or needs attention in any way'
                                   ))

write_xlsx(list(People=p6.recs,Charges=kr.hours.sum, Reviews=p6.reviews, TitleSheet=report.title), 
           paste("Report",ending,sep=''))

```

Below is example code for comparing kronos with p6 hours

#```{r}
roles.table <- get.roles.table()
person.comp.r <- left_join(person.comp, roles.table, by=join_by(role))

# by ctc by person adding month and fiscal year
tmp2.person.ctc<- person.comp.r %>% ungroup() %>%
  select(src,Last.Name, ctc, week, ihours=hours) %>%
  group_by(src,Last.Name, ctc, week)%>% summarise(hours=sum(ihours)) %>%
  arrange(src,Last.Name, ctc,  week) %>% 
  group_by(src,Last.Name, ctc) %>% mutate(chours=cumsum(hours)) %>%
  mutate(month=floor_date(week,unit="month",week_start=1)) %>%
  mutate(quarter=floor_date(week,unit="quarter",week_start=1)) %>%
  mutate(FY.orig=fiscal.from.date(week), FY=fiscal.date.adjust(week,FY.orig))

tmp2.person.ctc.sum.qtr <- tmp2.person.ctc %>% 
  group_by(src,Last.Name, FY, ctc, week) %>%
  summarise(tot.hours=sum(hours))


tmp2.pc.qtr.sum<- full_join(filter(tmp2.person.ctc.sum.qtr, src=="kronos"),
                            filter(tmp2.person.ctc.sum.qtr, src=="p6"),
                            suffix=c(".kr",".p6"),
                            by=join_by(Last.Name, FY, ctc, week)) %>%
  select(-starts_with("src.")) %>% ungroup()

tmp2.pc.qtr.sum <- tmp2.pc.qtr.sum %>% 
    mutate(Scheduled=!is.na(tot.hours.p6)) %>%
  mutate(total.p6=replace_na(tot.hours.p6,0),
         total.kr=replace_na(tot.hours.kr,0),
         Diff=total.p6-total.kr,
         Frac=total.kr/total.p6)

#write_xlsx(tmp2.pc.qtr.sum, paste("HoursJoined",ending,sep=''))

person.tasks.FY25<- labor$by.week.all %>% filter(week>=filt.st&week<filt.en) %>%
  #filter(FY %in% c(2024)) %>%
  mutate(month=floor_date(week,unit="month",week_start=1)) %>%
  mutate(quarter=floor_date(week,unit="quarter",week_start=1)) %>%
  mutate(LOE=ctc=='Q1903.01')%>%
    mutate(role.new=if_else(LOE=='TRUE'&Role!="RA", "LOE", Role)) %>%
  mutate(Full.Name=if_else(is.na(person),role.new,person)) %>%
  mutate(Last.Name=toupper(str_split_i(Full.Name,", ",i=1))) %>% 
  select(-Full.Name) %>% 
  left_join(all$all.data%>% select(task_id, task_code=code, task_name=name), join_by(task_id)) %>% 
  mutate(hours=dl.hours, activity=paste(task_code,task_name), 
         start=s, finish=e)


person.tasks.FY25.sum <- person.tasks.FY25 %>%
  group_by(week, ctc, Last.Name, task_id) %>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  #filter(!is.na(person)) %>%
  #left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person) ) %>%
  left_join(all$all.data%>% select(task_id, code, name), join_by(task_id))

person.tasks.merged <- left_join(tmp2.pc.qtr.sum, person.tasks.FY25.sum, by=join_by(week, ctc, Last.Name))

#write_xlsx(person.tasks.FY25, paste("LaborTasks",ending,sep=''))
#write_xlsx(person.tasks.merged, paste("HoursJoinedTasks",ending,sep=''))


#```

