---
title: "R Notebook"
output: html_notebook
---


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(writexl)
library(stringr)
library(rlang)
library(lubridate)

library(MAGIS100PM)
```


```{r}
sched.name <- "WS2503"
sched.base <- "BL2412"

#all <- get.all.schedule("BLBCR")
all <- get.all.schedule(sched.name)
all <- apply.baseline.schedule(all, sched.base)
charges <- get.all.kronos()
people <- get.p6.people(charges, all)
tasks.people <- combine.tasks.people(people, all)
```

```{r}
labor <- bin.labor(tasks.people)
costs <- bin.expenses(all$all.data)
```

#  ```{r}
# FY low = 2023, FY high = 2028
costs.week <- costs$target.by.week%>% filter(FY>=2024&FY<2026)%>%group_by(FY)%>%mutate(csum=cumsum(hsum))
costs.week.type.FY25 <- left_join(costs$target.by.month, all$all.data %>% select(code, rsrc_type), by=join_by(code)) %>%
  filter(FY==2025)
costs.week.ctc.FY25 <- left_join(costs$target.by.month.ctc, all$all.data %>% select(code, rsrc_type), by=join_by(code)) %>%
  filter(FY==2025)
costs.week.ctc.FY26 <- left_join(costs$target.by.month.ctc, all$all.data %>% select(code, rsrc_type), by=join_by(code)) %>%
  filter(FY==2026)
costs.week.ctc.FY27 <- left_join(costs$target.by.month.ctc, all$all.data %>% select(code, rsrc_type), by=join_by(code)) %>%
  filter(FY==2027)
costs.FY25.sum <- costs.week.type.FY25 %>% group_by(rsrc_type) %>% summarise(tot=sum(hsum))
costs.FY25.sum.ctc <- costs.week.ctc.FY25 %>% group_by(rsrc_type, ctc) %>% summarise(tot=sum(hsum))
costs.FY26.sum.ctc <- costs.week.ctc.FY26 %>% group_by(rsrc_type, ctc) %>% summarise(tot=sum(hsum))
costs.FY27.sum.ctc <- costs.week.ctc.FY27 %>% group_by(rsrc_type, ctc) %>% summarise(tot=sum(hsum))
#print(sum(costs.FY25.sum$tot))
#print(costs.FY25.sum)

costs.FY252627 <- bind_rows(FY25=ungroup(costs.FY25.sum.ctc), FY26=ungroup(costs.FY26.sum.ctc), FY27=ungroup(costs.FY27.sum.ctc),.id="FY")

print(costs.FY25.sum.ctc)
print(costs.FY26.sum.ctc)
print(costs.FY27.sum.ctc)
#  ```





This next one is most useful - This is a type-person-task report that is written out
# ```{r}
#labor <- bin.labor(tasks.people)

tpt.FY<- labor$by.week.person.task %>%
  filter(FY>2022) %>%
  group_by(type,person,task_id, FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  #filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person)) %>%
  left_join(all$tasks%>%select(task_id, task_name, task_code, target_start_date, target_end_date), by=join_by(task_id))
write_xlsx(tpt.FY%>% filter(FY %in% c(2025)), paste(base.path,"output/TPT_FY25.xlsx",sep=''))

# ```


Below is the more important quantities.
```{r}
filt.st<-as.Date("2024-10-01")
filt.en<-as.Date("2025-10-01")
filt.asof<- filt.st
#filt.st<-as.Date("2023-10-01")
#filt.en<-as.Date("2028-01-01")
#nfilt.asof<- as.Date("2023-10-01")
filt.name<- "PersonCTC"


p6.tmp<- labor$by.week.ctc %>% ungroup() %>% filter(week>=filt.st&week<filt.en) %>%
    select(week, hours=dl.hours, Full.Name=person, department=code, ctc=ctc, role=Role) %>%
    mutate(LOE=ctc=='Q1903.01')%>%
    mutate(role.new=if_else(LOE=='TRUE'&role!="RA", "LOE", role)) %>%
  mutate(Full.Name=if_else(is.na(Full.Name),role.new,Full.Name)) %>%
  mutate(Last.Name=toupper(str_split_i(Full.Name,", ",i=1))) %>% 
  select(-Full.Name)

# this is nearly the same as kro
kr.tmp<- charges %>% filter(Timecard.Start>=filt.asof&Timecard.Start<filt.en) %>%
    select(Last.Name, week=Timecard.Start, hours=Hours, ctc=taskcode, department=DSC, role=Role) %>%
    mutate(LOE=ctc=='Q1903.01') %>%
    mutate(role.new=if_else(LOE=='TRUE'&!is.na(ctc), "LOE", role))

person.comp <- bind_rows(p6=p6.tmp, kronos=kr.tmp, .id="src")


```



This is all the labor summaries that I use now.
Remember that person.comp is filtered by the time internal we are interested in.
```{r}

roles.table <- get.roles.table()

person.comp.r <- left_join(person.comp, roles.table, by=join_by(role))

tmp2a<- person.comp.r %>% ungroup()  %>%
  select(src, week, ihours=hours) %>%
  group_by(src, week)%>% summarise(hours=sum(ihours)) %>%
  arrange(src,  week) %>% 
  group_by(src) %>% mutate(chours=cumsum(hours))

# by week
tmp2<- person.comp.r %>% ungroup() %>% filter(ctc!="Q1903.01") %>%
  select(src, week, ihours=hours) %>%
  group_by(src, week)%>% summarise(hours=sum(ihours)) %>%
  arrange(src,  week) %>% 
  group_by(src) %>% mutate(chours=cumsum(hours))

# by role by week
tmp2.r<- person.comp.r %>% ungroup() %>% filter(ctc!="Q1903.01") %>%
  select(src,role.type, week, ihours=hours) %>%
  group_by(src,role.type, week)%>% summarise(hours=sum(ihours)) %>%
  arrange(src,role.type,  week) %>% 
  group_by(src,role.type) %>% mutate(chours=cumsum(hours))

# by category by week
tmp2.c<- person.comp.r %>% ungroup() %>% filter(ctc!="Q1903.01") %>%
  select(src,role.cat, week, ihours=hours) %>%
  group_by(src,role.cat, week)%>% summarise(hours=sum(ihours)) %>%
  arrange(src,role.cat,  week) %>% 
  group_by(src,role.cat) %>% mutate(chours=cumsum(hours))

# by role by category by week
tmp2.rc<- person.comp.r %>% ungroup() %>% #filter(ctc!="Q1903.01") %>%
  select(src,role.type, role.cat, week, ihours=hours) %>%
  group_by(src,role.type, role.cat, week)%>% summarise(hours=sum(ihours)) %>%
  arrange(src,role.type, role.cat,  week) %>% 
  group_by(src,role.type, role.cat) %>% mutate(chours=cumsum(hours))

# by role by ctc
tmp2.ctc<- person.comp.r %>% ungroup() %>% filter(ctc!="Q1903.01") %>%
  select(src,ctc, week, ihours=hours) %>%
  group_by(src,ctc, week)%>% summarise(hours=sum(ihours)) %>%
  arrange(src,ctc,  week) %>% 
  group_by(src,ctc) %>% mutate(chours=cumsum(hours))

# by ctc by person adding month and fiscal year
tmp2.person.ctc<- person.comp.r %>% ungroup() %>%
  select(src,Last.Name, ctc, week, ihours=hours) %>%
  group_by(src,Last.Name, ctc, week)%>% summarise(hours=sum(ihours)) %>%
  arrange(src,Last.Name, ctc,  week) %>% 
  group_by(src,Last.Name, ctc) %>% mutate(chours=cumsum(hours)) %>%
  mutate(month=ceiling_date(week,unit="month",week_start=1)) %>%
  mutate(quarter=ceiling_date(week,unit="quarter",week_start=1)) %>%
  mutate(FY.orig=fiscal.from.date(week), FY=fiscal.date.adjust(week,FY.orig))


```


Next section is plotting of the above quantities
```{r}

person.g4a<- ggplot(tmp2a,aes(x=week, y=chours, colour=src)) + 
  geom_line() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(name="cumulative hours",n.breaks=6) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y")+
  ggtitle("All hours with LOE")

print(person.g4a)


person.g4<- ggplot(tmp2,aes(x=week, y=chours, colour=src)) + 
  geom_line() +
  #scale_color_hue(labels = c("Kronos", "p6")) +
  theme(axis.text.x = element_text(angle = 90)) +
  #facet_wrap(vars(department),scales="free_y") + 
  scale_y_continuous(name="cumulative hours",n.breaks=6) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y")+
  ggtitle("All hours without LOE")

print(person.g4)
```


```{r}
person.g8<- ggplot(tmp2.ctc,aes(x=week, y=chours, colour=src)) + 
  geom_line() +
  #scale_color_hue(labels = c("Kronos", "p6")) +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(vars(ctc),scales="free_y") + 
  scale_y_continuous(name="cumulative hours",n.breaks=6) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y")+
  ggtitle("Hours by CTC without LOE")


print(person.g8)
ggsave(person.g8, filename=paste(base.path,"/output/ctc_hours.pdf",sep=''), units="in", device="pdf")

person.g5<- ggplot(tmp2.r,aes(x=week, y=chours, colour=src)) + 
  geom_line() +
  #scale_color_hue(labels = c("Kronos", "p6")) +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(vars(role.type),scales="free_y") + 
  scale_y_continuous(name="cumulative hours",n.breaks=6) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y")+
  ggtitle("Hours by role type without LOE")


print(person.g5)

person.g6<- ggplot(tmp2.c,aes(x=week, y=chours, colour=src)) + 
  geom_line() +
  #scale_color_hue(labels = c("Kronos", "p6")) +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(vars(role.cat),scales="free_y") + 
  scale_y_continuous(name="cumulative hours",n.breaks=6) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y")+
  ggtitle("Hours by role category without LOE")

print(person.g6)

person.g7<- ggplot(tmp2.rc,aes(x=week, y=chours, colour=src)) + 
  geom_line() +
  #scale_color_hue(labels = c("Kronos", "p6")) +
  theme(axis.text.x = element_text(angle = 90)) +
  facet_wrap(vars(role.type, role.cat),scales="free_y") + 
  scale_y_continuous(name="cumulative hours",n.breaks=6) +
  scale_x_date(name="Date (by month)", date_breaks='1 month', date_labels = "%b %y")+
  ggtitle("Hours by role type and category with LOE")

print(person.g7)

```

```{r}
tmp2.ra<- person.comp.r %>% ungroup()  %>%
  select(src, Last.Name, week, ihours=hours) %>%
  group_by(src, Last.Name, week)%>% summarise(hours=sum(ihours)) %>%
  arrange(src, Last.Name,  week) %>% 
  group_by(src, Last.Name) %>% mutate(chours=cumsum(hours))

tmp.g <- ggplot(tmp2.ra %>% 
                  filter(str_detect(Last.Name, "NOBREGA|CURFMAN|FUNK|HURD|KELLETT|MURP|SANTU"))
                , aes(x=week, y=chours, colour=src)) + 
  geom_line() +
  facet_wrap(vars(Last.Name),scales="free_y", nrow=3) +
  scale_x_date(name="Date", date_breaks='1 month', date_labels = "%b %y") +
  scale_y_continuous(name="cumulative hours", n.breaks=6) +
        theme(axis.text.x = element_text(angle = 90))

tech.names <- "FEDERWITZ|KELLETT|CASTILLO URIBE|ROGERS|WILLIAMS|LOPEZ|FLANAGAN|MONTIEL"


tmp.gt <- 
ggplot(tmp2.ra %>% filter(str_detect(Last.Name, tech.names))
                , aes(x=week, y=chours, colour=src)) + 
  geom_line() +
  facet_wrap(vars(Last.Name),scales="free_y", nrow=3) +
  scale_x_date(name="Date", date_breaks='1 month', date_labels = "%b %y") +
  scale_y_continuous(name="cumulative hours", n.breaks=6) +
        theme(axis.text.x = element_text(angle = 90))

  
print(tmp.g)
print(tmp.gt)
```

By-hand assignments:

        role.p6            role.kr          role.type     role.cat
1       Op Specialist               <NA>   Specialist      Exp
2       Project Cntls      Project Cntls         Proj     Proj
3            Eng Phys               <NA>   Specialist      Exp
4  Particle Physicist Particle Physicist         Phys     Phys
5            Mech Eng           Mech Eng          Eng     Mech
6                  PM                 PM         Proj     Proj
7                  RA                 RA         Phys     Phys
8         Mech Design        Mech Design Design/Draft     Mech
9          Mech Draft               <NA> Design/Draft     Mech
10          Mech Tech          Mech Tech         Tech     Mech
11    Electrical Tech    Electrical Tech         Tech     Tech
12     Electrical Eng     Electrical Eng          Eng     Elec
13      App Developer               <NA>        Other    Other
14        Metrologist               <NA>        Other      Exp
15               <NA>          Civil Eng        Other      ISD
16               <NA>     Accel Sys Spec   Specialist      Exp
17               <NA>    Construct Coord        Other      ISD
18               <NA>    Electrical Task         Tech     Elec
19               <NA>          Geodesist        Other      ISD
20               <NA>      High Vac Tech         Tech      Exp



----------------------- less useful stuff is below ---------------

Next are two spreadsheet summaries that are written out
```{r}
persons.FY232425<- labor$by.week.person %>%
  filter(FY %in% c(2023,2024,2025)) %>%
  group_by(person,FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name),join_by(person) )
#write_xlsx(persons.FY232425, paste(base.path,"persons_FY232425.xlsx",sep=''))

types.FY232425<- labor$by.week.all %>%
  filter(FY %in% c(2023,2024,2025)) %>%
  group_by(type,person, FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  #filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person) )
#write_xlsx(types.FY232425, paste(base.path,"types_FY232425.xlsx",sep=''))


#  mutate(FY.orig=fiscal.from.date(week), FY=fiscal.date.adjust(week,FY.orig))

person.tasks.FY25<- labor$by.week.all %>%
  filter(FY %in% c(2025)) %>%
  group_by(type, person, task_id, FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  #filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person) ) %>%
  left_join(all$all.data%>% select(task_id, code, name), join_by(task_id))
#write_xlsx(person.tasks.FY25, paste(base.path,"tasks_FY25.xlsx",sep=''))

person.tasks.ctc.FY25<- labor$by.week.all %>%
  filter(FY %in% c(2025)) %>%
  group_by(type, person, task_id, ctc, FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  #filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person) ) %>%
  left_join(all$all.data%>% select(task_id, code, name), join_by(task_id))
#write_xlsx(person.tasks.ctc.FY25, paste(base.path,"tasks_ctc_FY25.xlsx",sep=''))

person.tasks.ctc.FY26<- labor$by.week.all %>%
  filter(FY %in% c(2026)) %>%
  group_by(type, person, task_id, ctc, FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  #filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person) ) %>%
  left_join(all$all.data%>% select(task_id, code, name), join_by(task_id))
#write_xlsx(person.tasks.ctc.FY26, paste(base.path,"tasks_ctc_FY26.xlsx",sep=''))

person.tasks.ctc.FY27<- labor$by.week.all %>%
  filter(FY %in% c(2027)) %>%
  group_by(type, person, task_id, ctc, FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  #filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person) ) %>%
  left_join(all$all.data%>% select(task_id, code, name), join_by(task_id))
#write_xlsx(person.tasks.ctc.FY27, paste(base.path,"tasks_ctc_FY27.xlsx",sep=''))

```

```{r}
persons.FY25<- labor$by.week.person %>%
  filter(FY %in% c(2025)) %>%
  group_by(person,FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805)) %>%
  filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name),join_by(person) )
#write_xlsx(persons.FY25, paste(base.path,"persons_FY25.xlsx",sep=''))
```

This is the section for looksing at the labor in the schedule by week by person.
It also has the dataset for looking at labor per resource category (ENG, SCI, TECH).

The resources.plot() is used to checking resource leveling (with or without LOE).


```{r}

# select(week, hours=dl.hours, Full.Name=person, department=code, ctc=ctc, role=Role)

# handling of FY24 for summary purposes
person.tasks.FY25<- labor$by.week.all %>%
  filter(FY > 2024) %>%
  mutate(month=floor_date(week,unit="month",week_start=1)) %>%
  mutate(quarter=floor_date(week,unit="quarter",week_start=1)) %>%
  mutate(LOE=ctc=='Q1903.01')%>%
    mutate(role.new=if_else(LOE=='TRUE'&Role!="RA", "LOE", Role)) %>%
  mutate(Full.Name=if_else(is.na(person),role.new,person)) %>%
  mutate(Last.Name=toupper(str_split_i(Full.Name,", ",i=1))) %>% 
  select(-Full.Name) %>%
  rename(hours=dl.hours, target_start=s, target_end=e) %>% 
  left_join(all$all.data%>% select(task_id, code, name), join_by(task_id))

person.tasks.FY25.sum <- person.tasks.FY25 %>%
  filter(!str_detect(name,"LOE")) %>%
  group_by(FY, week, rsrc) %>%
  summarise(hsum=sum(hours)) %>% 
  mutate(ftes=hsum/(1805))
  #filter(!is.na(person)) %>%
  #left_join(people%>%select(person=role_name, type=rsrc_name, DSC),join_by(type,person) ) %>%
  #left_join(all$all.data%>% select(task_id, code, name), join_by(task_id))

t2<-resources.plot(person.tasks.FY25.sum)
print(t2)

#person.tasks.FY25 %>% 
#  filter(str_detect(name,"LOE")) %>%
#  group_by(FY, week, rsrc, Last.Name) %>%
#  summarise(hsum=sum(hours)) %>% view()

person.tasks.FY25.sum2 <- person.tasks.FY25 %>%
  filter(!str_detect(name,"LOE")) %>%
  group_by(FY, week, rsrc, code.y, name) %>%
  summarise(hsum=sum(hours)) 

write_xlsx(person.tasks.FY25, paste(base.path,"AllYearCR/labor_rsrc.xlsx",sep=''))
write_xlsx(person.tasks.FY25.sum, paste(base.path,"AllYearCR/labor_rsrc_sum.xlsx",sep=''))
write_xlsx(person.tasks.FY25.sum2, paste(base.path,"AllYearCR/labor_sum_task.xlsx",sep=''))

```


------------ notes --------------

#req %>% distinct(Name) %>% pull() %>% str_split_i(", ",i=1) %>% toupper()
# use charges$Last.Name for join

#by.day.grouped<- tasks.with.all %>%
#    filter(rsrc_type.x=='RT_Labor') %>%
#    select( task_id=task_id,s=target_start_date, e=target_end_date, dt=target_qty, r=remain_qty,  person=role_name, #rsrc=rsrc.code, type=rsrc_name, code=DSC, ctc=ctc, Role=Role, Specialty=Specialty) %>%
    #filter(!is.na(ctc)&str_detect(ctc,".*")) %>%
#    rowwise() %>% mutate(dl=list(dates.list.days(s,e,dt)))

#  by.day<- unnest(by.day.grouped,cols=c(dl),names_sep='.') %>% arrange(s) %>%
#    mutate(week=ceiling_date(dl.d,unit="week",week_start=1)) %>%
#    mutate(FY.orig=fiscal.from.date(week), FY=fiscal.date.adjust(week,FY.orig))


 This is notes on all the fields that would be interesting to add (role and ctc)
 across the three areas of requests, charges, and schedule.
 There are not distinct combos of (Last.Name, ctc, role) for some of the entries
 which is something that needs to be thought through.
 
charges%>%distinct(Function.Category) %>% view() # don't use
charges%>%distinct(Function.Role) %>% view() # role
charges%>%distinct(taskcode) %>% view() # ctc
req%>%distinct(ResourceRole) # role
req %>% distinct(ProjectTask) # ctc
labor$by.week.ctc %>% ungroup() %>% distinct(Role) # role
labor$by.week.ctc %>% ungroup() %>% distinct(ctc) # ctc

role.trans <- full_join(
  p6.tmp %>% distinct(role),
  kr.tmp %>% distinct(role),
  by=join_by(role), keep=TRUE, suffix=c(".p6",".kr"))
------------------


These two are not currently used.
```{r}

persons.FY23Q34<- labor$by.week.person %>%
  filter(FY==2023)%>%
  filter(week %within% interval('2023-07-01','2023-10-01')) %>%
  group_by(person,FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805/4)) %>%
  filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, div=DSC),join_by(person) )

persons.FY24Q1<- labor$by.week.person %>%
  filter(FY==2023)%>%
  filter(week %within% interval('2023-07-01','2024-03-12')) %>%
  group_by(person,FY)%>%
  summarise(hrs=sum(dl.hours)) %>% 
  mutate(ftes=hrs/(1805/4)) %>%
  filter(!is.na(person)) %>%
  left_join(people%>%select(person=role_name, type=rsrc_name, div=DSC),join_by(person) )
```

# unused stuff below

This next section is not information that I use now.
```{r}

req <- read_xlsx("../input/LaborRequestFrom202306.xlsx")

req<- req %>% 
  mutate(start=as.Date("2023-10-01"), end=as.Date("2024-09-30"), hours.per.year=fermi.FTE*Request,
         Last.Name=toupper(str_split_i(Name,", ",i=1))
)

req.rows<- req %>% rowwise() %>% mutate(dl=list(dates.list.days(start,end,hours.per.year)))

req.by.day <- unnest(req.rows, cols=c(dl),names_sep='_') %>% arrange(start) %>%
  mutate(week=ceiling_date(dl_d, unit="week", week_start=1))

req.by.week <- req.by.day %>% filter(week>=filt.st & week<filt.en) %>%
  group_by(Last.Name, week) %>% summarise(hours=sum(dl_hours)) %>% 
  ungroup() %>% arrange(Last.Name, week) %>% group_by(Last.Name) %>%
  mutate(chours=cumsum(hours))



# I don't think I need Timecase.End.
kro <- charges %>% filter(Timecard.Start>=filt.asof & Timecard.Start<filt.en) %>% 
  select(week=Timecard.Start, Last.Name, Charged.Hours=Hours) %>% 
  group_by(Last.Name, week) %>% summarize(hours=sum(Charged.Hours)) %>% ungroup() %>%
  arrange(Last.Name,week) %>% group_by(Last.Name) %>% 
  mutate(chours=cumsum(hours))


req.kro <- full_join(req.by.week%>%filter(week<=filt.en), kro, by=join_by(Last.Name, week), suffix=c(".budget",".kronos"))

# recalculate cumulative hours
req.kro <- req.kro %>% arrange(Last.Name, week) %>% group_by(Last.Name) %>%
  mutate(hours.kronos=if_else(is.na(hours.kronos),0,hours.kronos), chours.kronos=cumsum(hours.kronos)) %>%
  mutate(perc=chours.kronos/chours.budget)


write_xlsx(req.kro, paste(base.path,"output/BudgetVersusKronos.xlsx",sep=''))

```


The CompHours spreadsheet is important.  What's important, I think, 
is the difference in hours between P6 and kronos over the quarter.
The difficult question that may not have an answer is, what were those
hours used for?


```{r}

good.names <- charges%>%select(Last.Name, department=DSC) %>% distinct() %>% filter(department %in% c("ESH","ISD","FESS","ESHQ")) %>% pull(Last.Name)

good.names <- c("NOBREGA","CURFMAN","FUNK","HURD","KELLETT",
                "KOWALKOWSKI", "KIBURG", "PLUNKETT")

#good.names <- "NOBREGA|CURFMAN|FUNK|HURD|KELLETT|KOWAL|KIBURG|PLUNK|UNNAMED|MECH|SPECI|METRO|PARTICLE|SAFETY"


# p6.tmp%>% filter(Hours>0) %>% group_by(department,Full.Name) %>% summarize(tot=sum(Hours)) %>% arrange(Full.Name,department) %>% view()

calc_hour_diffs <- function(a,b)
{
  if_else(is.na(a),0.0,a) - if_else(is.na(b),0.0,b)
}

hours.per.person.per.week <- person.comp %>% ungroup() %>% filter(week>=filt.asof) %>%
  select(src,week, Last.Name, ctc, hours) %>%
  group_by(src, Last.Name, week) %>% summarize(hours=sum(hours)) %>% ungroup() %>%
  arrange(src, Last.Name, week) %>% group_by(src, Last.Name) %>% mutate(chours=cumsum(hours))

comp.hours <- bind_rows(req.by.week %>% mutate(src="request"), 
                        hours.per.person.per.week) 

comp.hours.diff <- pivot_wider(comp.hours, names_from=c("src"), values_from=c("hours", "chours")) %>%
  mutate(hours_kronos=if_else(is.na(hours_kronos),0.0, hours_kronos), diff.kp=hours_kronos-hours_p6) %>%
  filter(Last.Name%in%good.names)

comp.hours.sum<- comp.hours%>% group_by(src,Last.Name) %>% summarize(total.hours=sum(hours)) %>% 
  pivot_wider(names_from=c("src"),values_from=c("total.hours")) %>% 
  arrange(Last.Name) %>% mutate(diff=calc_hour_diffs(kronos,p6))

write_xlsx(comp.hours.sum,paste(base.path,"output/CompHours_",filt.name,".xlsx",sep=''))


g3<- ggplot(comp.hours, aes(x=week, y=chours,colour=src)) +facet_wrap(vars(Last.Name),scales="free_y") + geom_line()
#g4<- ggplot(comp.hours.diff, aes(x=week, y=diff.kp)) +facet_wrap(vars(Last.Name),scales="free_y",ncol=1) + geom_line()

#print(g3)
#print(g4)
```

```{r}
#tasks.people %>% filter(target_start_date<as.Date("2025-01-01")) %>%
#  select(task_id, rsrc_id, role_id, target_start_date, target_end_date, rsrc_type.x, rsrc_name, role_name, target_cost)%>%
#  filter(str_detect(rsrc_name, "Electric")) %>%
#  left_join(all$all.data%>%select(task_id, name, code, total_float), by=join_by(task_id)) %>%
#  arrange(target_start_date) %>% 
#  view()

all$tasks %>% filter(plan_start_date<as.Date("2025-01-01")) %>% 
  select(task_id, rsrc_id, plan_start_date, plan_end_date, task_code, task_name) %>%
  left_join(all$taskrsrc%>% select(rsrc_id, role_id, rsrc_type), by=join_by(rsrc_id)) %>%
  left_join(all$roles%>%select(role_id, role_name), by=join_by(role_id)) %>%
  view()

# from all_plots:
proc<- procurements.plot(all, st=Sys.Date()-weeks(9*4), en=Sys.Date()+weeks(8*4))

# only show relevant things:
proc$data%>% select(task_code, task_name, total_cost, target_start_date, target_end_date, plan_start_date, plan_end_date, state, status_code, act_start_date) %>% view()

tasks.people %>% select(task_id,target_qty, remain_qty, role_name, rsrc_name) %>% left_join(all$tasks%>% select(task_id,task_code, task_name), join_by(task_id)) %>%view()
```
Do the summary by quarter, person, ctc

```{r}
tmp2.person.ctc %>% group_by(src,Last.Name, FY, ctc, month) %>%
  summarise(tot.hours=sum(hours)) %>%
view()

```

look at all the unstarted tasks

```{r}

select(all$all.data, code, name, rsrc_type, status, target_start, target_end, area, total_cost, total_float) %>% 
  mutate(total_float=total_float/8) %>%
  filter(target_start>as.Date("2024-07-01") & target_start<as.Date("2025-10-01")) %>% 
  filter(status!="TK_Complete", area>1) %>% 
  arrange(target_start) %>% view("CR3") %>% write_xlsx("activities202407-202510CR3.xlsx")
```

```{r}
jbk.acts <- read_xlsx("activities202407-202503.xlsx") %>% 
  mutate(new.group=if_else(priority<4, 'H', if_else(priority<7, 'M', 'L'))) 

jbk.acts %>% group_by(new.group) %>% summarise(tot=sum(total_cost, na.rm=TRUE))

jbk.acts %>% filter(target_start< as.Date("2024-10-01")) %>% ungroup() %>% group_by(new.group) %>% summarise(tot=sum(total_cost,na.rm=TRUE))

```


```{r}

#CR3.hours.joined<- tmp2.pc.qtr.sum
#NoCR.hours.joined<- tmp2.pc.qtr.sum

full_join(CR3.hours.joined%>% select(week, ctc, Last.Name, total.p6), NoCR.hoursJoined%>% select(week, ctc, Last.Name, total.p6), by=join_by(week, ctc, Last.Name), suffix=c(".CR", ".NoCR"))%>% mutate(Diff=total.p6.CR-total.p6.NoCR, perc=total.p6.CR/total.p6.NoCR) %>% write_xlsx("HoursJoined_CR_NoCR2.xlsx")

```


```{r}

# bind_rows( jbk.2.CR, jbk.2.NoCR,.id=c("CR", "noCR"))

reduce_tasks <- function(x)
{
  x %>% filter(week<filt.en & week>filt.st) %>% select(week, code, name, hsum) %>%
    group_by(code, name) %>% summarise(count=n(), tot=sum(hsum))
}

full_join( reduce_tasks(jbk.2.CR), 
           reduce_tasks(jbk.2.NoCR), 
           suffix=c(".CR", ".noCR"), by=join_by(code)) %>%
      mutate(dropped=is.na(name.CR)) %>% 
    view() %>% write_xlsx("CR_dropped_activities.xlsx")

```

