---
title: "R Notebook"
output: html_notebook
---

```{r message=FALSE, warning=TRUE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(writexl)
library(stringr)
library(lubridate)

library(MAGIS100PM)
```


This is a comparison between two schedules

```{r}
all <- get.all.schedule("WS2309")
all <- apply.baseline.schedule(all, "BCRBL2")
charges <- get.all.kronos()
people <- get.p6.people(charges, all)
tasks.people <- combine.tasks.people(people, all)
```

More random stuff:
This code does not work on my Windows system for running python chunks.

library(reticulate)
Sys.setenv(RETICULATE_PYTHON = "/Users/jimk/AppData/Local/Microsoft/WindowsApps/PythonSoftwareFoundation.Python.3.11_qbz5n2kfra8p0")
use_python("/Users/jimk/AppData/Local/Microsoft/WindowsApps/PythonSoftwareFoundation.Python.3.11_qbz5n2kfra8p0", required=TRUE)

#```{python}
#print("the")
#python.exe xer_extractor.py -x current
#python.exe reader.py -d -x current -S
#```


Extract T0, T1, T2 milestones.

```{r}
print(getwd())
tmp.ims<-all$all.data%>%filter(str_detect(name,"^T0|^T1|^T2"))%>%select(code, name, target_end)
tmp.ims.templ<-read_excel("../MOA_PMP/IntermediateMilestonesTemplate.xlsx")
tmp.both<- tmp.ims.templ %>% left_join(tmp.ims, join_by(Activity==code))
write_xlsx(tmp.both%>%select(Activity, Name=name, Date=target_end, Tier, Section, Group),"../output/tmp-milestones.xlsx")
```

Really random stuff: show how dates work.

```{r}
fquarter<- function(x) { quarter(x, fiscal_start=10, type="date_first") }
lquarter<- function(x) { quarter(x, fiscal_start=10, type="date_last") }
quarter(Sys.Date()+months(1), fiscal_start = 10, type="year.quarter")
quarter("2023-07-07", fiscal_start = 10, type="date_first")
tmp.df<- fquarter(Sys.Date())
tmp.dl<- lquarter(Sys.Date())
print(tmp.df)
print(tmp.dl)

fquarter(tmp.df-months(1))
fquarter(tmp.dl+months(1))

floor_date(as.Date("2023-11-04"), unit="month")-months(1)
```


This block below is all special code that really only needs to be run once or for testing.

```{r}
#all$all.data %>% 
#  mutate(yr=fiscal.from.date(target_start), days_float=total_float/8) %>%
#  filter(yr>2023) %>%
#  select(code, name, target_start, target_end, total_float, total_cost,yr, days_float) %>%
#  arrange(target_start) %>%
#  view()

# prime the rolesmap here (only needed once, then hand edited)
#rolesmap<-rbind(
#  data.frame(role=unique(charges$Function.Role))%>%mutate(type='kr'),
#  data.frame(role=unique(labor$by.week.person$type))%>%mutate(type='p6')
#)
#write_xlsx(rolesmap,"../rolesmap.xlsx")

#ctcmap<- read.csv("../ctcmap.csv",colClasses=c("character","character","character"), strip.white=TRUE)
#save(ctcmap, file="../MAGIS100PM/data/ctcmap.rda",version=2)

#rolesmap<- read_xlsx("../rolesmap.xlsx")
#save(rolesmap, file="../MAGIS100PM/data/rolesmap.rda",version=2)

#roles<- read.csv("../roles.csv", strip.white=TRUE)
#save(roles, file="../MAGIS100PM/data/roles.rda",version=2)


```


Extract procurements for FY24.
```{r}
sti <- as.Date("2023-10-01")
proc<- procurements.filter(all, st= sti-months(2), en=sti+months(12))
procs <- proc$data %>%
  select(task_code, task_name, state, status_code, total_cost, target_start_date, target_end_date, area) %>%
  filter(total_cost>0) %>% arrange(target_start_date) %>%
  left_join(MAGIS100PM::ctcmap%>%filter(level=="L1")%>%mutate(area=as.integer(wbs)), by=join_by(area))
#write_xlsx(procs, "../output/procurementsFY24.xlsx")
```

