---
title: "R Notebook"
output: html_notebook
---

```{r message=FALSE, warning=TRUE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(writexl)
library(stringr)
library(lubridate)
library(RColorBrewer)

library(MAGIS100PM)
```

```{r}
sched.name <- "WS2412"
sched.base <- "BL2409"

all <- get.all.schedule(sched.name)
all <- apply.baseline.schedule(all, sched.base)
charges <- get.all.kronos()

# test cleanup of charges, what distinct rows of Fermi.ID, Transaction.Date, Charge.Task.Code
# distinct(Fermi.ID, Transaction.Date, Charge.Task.Code, .keep_all=TRUE) %>% 
# this distinct thing is now in the library function get.all.kronos 

people <- get.p6.people(charges, all)
tasks.people <- combine.tasks.people(people, all)

labor <- bin.labor(tasks.people)
costs <- bin.expenses(all$all.data)
```

```{r}
#filt.st<-as.Date("2024-04-01")
#filt.en<-as.Date("2024-07-01")
#filt.name<- "FY24Q3"
#filt.st<-as.Date("2024-01-01")
#filt.en<-as.Date("2024-04-01")
#filt.name<- "FY24Q2"
#filt.st<-as.Date("2023-10-01")
#filt.en<-as.Date("2024-01-01")
#filt.name<- "FY24Q1"
filt.st<-as.Date("2024-09-29")
filt.en<-as.Date("2024-12-31")
filt.name<- "FY25Q1"

filt.asof<- filt.st
```

The Export spreadsheet comes from Sarah.
The HoursJoined comes from LaborSummariesTemplate.qmd.

Expenditure overhead with MSA or M&S is for material purchases
Expenditure overhead comes in many flavors:
 - FRINGE / PROGRAM SUPPORT
 - VAC / OPTO
 - MSA / M&S
 - CSS / G&A
 There are TIME WORKED MONTHLY and WEEKLY, POSTDOC, and CONSTRUCTION ENGINEERING.
 There are MATERIAL PURCHASES and FREIGHT.
 PROFESSIONAL SERVICES is Jan.
 
 ALLOC|FRINGE will get nearly all overhead.
 
 
 By the way, CSS = Common Site Support.

```{r warning=FALSE}
print(getwd())
tmp.taskcode.map <- read_xlsx("../CostVarianceAnalysis/TaskCodeMapping.xlsx")

#exported.all<- read_xlsx("../../finance/Export_Q1903_JUN-24_2024.xlsx",sheet="fnd_gfm_14805829") %>%
exported.all<- read_xlsx("../../finance/Export_Q1903_FY25 Q1_2025.01.17.xlsx",sheet="fnd_gfm_14953851") %>%
  select(Task,ExpendType=`Expnd Type`, ItemDate=`Item Date`, 
         Who=`Employee/Supplier`, Quantity, 
         FuncBurdenedCost=`Proj Func Burdened Cost`, 
         BurdenedCost=`Project Burdened Cost`, ExpendOrg=`Expnd Org`)  %>%
  mutate(person=str_split_i(Who,", ",i=1)) %>%
  mutate(org=str_split_i(ExpendOrg," - ",i=1), ctc_old=str_split_i(Task,".Q",i=1)) %>%
  mutate(q=quarter(ItemDate, fiscal_start=10), y=fiscal.year(ItemDate), m=fiscal.month(ItemDate)) %>%
  mutate(month=floor_date(ItemDate,unit="month",week_start=1)) %>%
  mutate(quarter=floor_date(ItemDate,unit="quarter",week_start=1)) %>% 
  left_join(tmp.taskcode.map, by=join_by(ctc_old)) %>% rename(ctc=ctc_new)



exported <- exported.all %>% filter(ItemDate>=filt.st, ItemDate<filt.en)
```

```{r}


# this is fixed: it is to gather the assigned area, desc, kind to each person
# this file covered FY24 through Q3
tmp.pl <- read_xlsx("../CostVarianceAnalysis/people_labels.xlsx", sheet="Sheet1") 
tmp.hr <- read_xlsx("../CostVarianceAnalysis/HoursJoined2024-09-292024-12-31_labeled.xlsx", sheet="Sheet3")%>% rename(person='Row Labels') 
person.area <- tmp.hr %>% select(person, Area, Desc, Kind)

exported <- exported %>%
  left_join(person.area, by=join_by(person))

# add ctc to this
# this file covered FY24 through Q3
tmp.hr.task <- read_xlsx("../CostVarianceAnalysis/HoursWeekTask2024-09-292024-12-31R.xlsx", sheet="Sheet1") %>%
  filter(week>=filt.st, week<filt.en) %>%
  mutate(q=quarter(week, fiscal_start=10), y=fiscal.year(week), m=fiscal.month(week)) %>%
  mutate(month=floor_date(week,unit="month",week_start=1)) %>%
  mutate(quarter=floor_date(week,unit="quarter",week_start=1)) %>%
  left_join(select(all$all.data, task_id, ctc, category, group), by=join_by(task_id)) 

tmp.hr.joined <- read_xlsx("../CostVarianceAnalysis/HoursJoined2024-09-292024-12-31R.xlsx", sheet="Sheet1") %>%
  filter(week>=filt.st, week<filt.en) %>%
  mutate(q=quarter(week, fiscal_start=10), y=fiscal.year(week), m=fiscal.month(week)) %>%
  mutate(month=floor_date(week,unit="month",week_start=1)) %>%
  mutate(quarter=floor_date(week,unit="quarter",week_start=1))

# only write if there are issues.
#write_xlsx(exported, "../CostVarianceAnalysis/ExportedLabeled.xlsx")
#write_xlsx(tmp.hr.task, "../CostVarianceAnalysis/HoursWeekTask.xlsx")
#write_xlsx(tmp.hr.joined, "../CostVarianceAnalysis/HoursJoined.xlsx")

```

Note: Temples and Vasonis come in from HoursJoined as Q1903.01 and Q1903.04, and in exported they come in as .06 and .05.

```{r warning=FALSE}

tmp.ex.sum <- exported %>% 
  group_by(y,q, ctc, person) %>% summarise(tot.cost=sum(BurdenedCost), tot.quant=sum(Quantity)) 
tmp.hr.sum <- tmp.hr.joined %>%
  group_by(y,q, ctc, Last.Name) %>% summarise(tot.p6=sum(total.p6), tot.kr=sum(total.kr), tot.diff=sum(Diff))
tmp.ex.hr <-tmp.ex.sum  %>% full_join(tmp.hr.sum, by=join_by(y,q,ctc,person==Last.Name))

# only write these out if there are issues.
#write_xlsx(tmp.ex.hr, "../CostVarianceAnalysis/JoinedExpP6.xlsx")

```

need to look at person-ExpendOrg-ctc-BurdenedCost 
to see if anyone is in multiple orgs. Also to see if all LOE can be filted out.
person-ExpendOrg is one-to-one.

Below is consistent with Q3 current period actual costs of $537K for Q1903.02 and .04.
The Q3 total hours from the export is 1058 not included Q1903.01.


The schedule HoursWorkTask sheet says there should have been 1940 hours worked.

HoursWorkTask has task_id, which links to tasksrc$taskid, 
links to roles\$role_name and rsrc\$rsrc_name

For export data:
Total hours with LOE:
Total hours without LOE:
Total cost of labor:
Total burden cost with LOE:
Total burden cost without LOE:


This needs to be updated per quarter print

```{r}

# total cost of everything
j.a<-exported %>% #filter(!str_detect(ctc,"Q1903.0[16]")) %>% 
  group_by(q,ExpendOrg,person, ctc) %>% summarise(tot=sum(BurdenedCost)) %>%
   ungroup() %>% group_by(q) %>% 
  summarise(all.tot=sum(tot))

# total cost of project without LOE
j.b<-exported %>% filter(!str_detect(ctc,"Q1903.0[16]")) %>% 
  group_by(q,ExpendOrg,person, ctc) %>% summarise(tot=sum(BurdenedCost)) %>%
  ungroup() %>% group_by(q) %>% 
  summarise(all.tot=sum(tot))

# total hours and burdened cost (without overhead) without LOE
j.c<-exported %>% ungroup() %>% filter(!str_detect(ctc,"Q1903.0[16]")) %>% 
  filter(str_detect(ExpendType, "TIME|ENGINEER|POST")) %>% 
  #group_by(person, ExpendType) %>%
  group_by(q) %>% 
  summarise(tot.q=sum(Quantity), tot.b=sum(BurdenedCost))

# total hours and burdened cost (without overhead) with LOE
j.d<-exported %>% ungroup() %>% #filter(ctc!='Q1903.xx') %>% 
  filter(str_detect(ExpendType, "TIME|ENGINEER|POST")) %>% 
  #group_by(person, ExpendType) %>%
  group_by(q) %>% 
  summarise(tot.q=sum(Quantity), tot.b=sum(BurdenedCost))

# M&S costs including overhead (no LOE)
j.e<-exported %>% ungroup() %>% filter(!str_detect(ctc,"Q1903.0[16]")) %>% 
  filter(str_detect(ExpendType, "MATERIAL|FREIGHT|MSA|M&S|PROFESS|CIVIL|TRAVEL|LABS|FABRI|EQUIP")) %>% 
  #group_by(person, ExpendType) %>% 
  group_by(q) %>% 
  summarise(tot.q=sum(Quantity), tot.b=sum(BurdenedCost))

# Costs/Hours excluding M&S (no LOE)
j.f<-exported %>% ungroup() %>% filter(!str_detect(ctc,"Q1903.0[16]")) %>% 
  filter(!str_detect(ExpendType, "MATERIAL|FREIGHT|MSA|M&S|PROFESS|CIVIL|TRAVEL|LABS|FABRI|EQUIP")) %>% 
  #group_by(person, ExpendType) %>%
  group_by(q) %>% 
  summarise(tot.q=sum(Quantity), tot.b=sum(BurdenedCost))

# Costs/Hours excluding M&S (with LOE)
j.g<-exported %>% ungroup() %>% #filter(!str_detect(ctc,"Q1903.0[16]")) %>% 
  filter(!str_detect(ExpendType, "MATERIAL|FREIGHT|MSA|M&S|PROFESS|CIVIL|TRAVEL|LABS|FABRI|EQUIP")) %>% 
  #group_by(person, ExpendType) %>%
  group_by(q) %>% 
  summarise(tot.q=sum(Quantity), tot.b=sum(BurdenedCost))

print(paste("Cost of everything:",j.a))
print(paste("Cost of everything no LOE:",j.b))
print(paste("Hours/Cost no overhead without LOE:",j.c[[1]],j.c[[2]]))
print(paste("Hours/Cost no overhead with LOE:",j.d[[1]],j.d[[2]]))
print(paste("Hours/Cost M&S with overhead no LOE:",j.e[[1]],j.e[[2]]))
print(paste("Hours/Cost no M&S, no LOE:",j.f[[1]],j.f[[2]]))
print(paste("Hours/Cost no M&S, with LOE:",j.g[[1]],j.g[[2]]))
```

```{r}
#exported.all %>% ungroup() %>% 
#  group_by(ExpendOrg, ItemDate, ExpendType, Who) %>% 
#  summarise(tot.cost=sum(BurdenedCost), tot.quant=sum(Quantity))  %>% view()

#exported %>% ungroup() %>% 
#  group_by(ExpendOrg) %>% 
#  summarise(tot.cost=sum(BurdenedCost), tot.quant=sum(Quantity))  %>% view()

ending <- paste(filt.st,filt.en,"R.xlsx",sep='')

cost.tab <- data.frame(ctc=c('Q1903.02','Q1903.04','Q1903.05','Q1903.08'),overhead=c(2.2,2.2,1.3,1.3))

charged.time.q3 <- exported %>% ungroup() %>% filter(!str_detect(ctc,'Q1903.0[16]')) %>% 
  filter(str_detect(ExpendType, "TIME|ENGINEER|POST")) %>%
  group_by(ExpendOrg, person, q,ctc, Area, Desc) %>% summarise(tot.hours=sum(Quantity), tot.cost=sum(BurdenedCost)) %>% 
  left_join(cost.tab, by=join_by(ctc)) %>% mutate(tot.val=tot.cost*overhead + tot.cost) 

# only write if there are issues
#write_xlsx(charged.time.q3, paste("q3_charged_time",ending, sep=''))

charged.time.q3 %>% view("charged_time") %>% ungroup() %>% summarise(rtot=sum(tot.val))

sum.hr.task <- tmp.hr.task %>% ungroup() %>% filter(ctc!="Q1903.01") %>%
  group_by(code, name) %>% summarise(tot.hours=sum(hsum)) #%>% 
#  view() %>% ungroup() %>% summarise(rtot=sum(tot.hours))

# look at M&S spending
exported %>% ungroup() %>% filter(!str_detect(ctc,"Q1903.0[16]")) %>%
 filter(str_detect(ExpendType, "MATERIAL|FREIGHT|MSA|M&S|PROFESS|CIVIL|TRAVEL|LABS")&!str_detect(org,"ISD|ETD")) %>% view('MS-spending')

exported %>% ungroup() %>% 
  filter(org=="ISD") %>% 
  filter(!str_detect(ExpendType, 'M&S|MSA|CIVIL|MATERIAL|FREIGHT')) %>% 
  group_by(ExpendOrg, Who, ExpendType) %>% 
  summarise(tot.cost=sum(BurdenedCost), tot.quant=sum(Quantity)) %>% view()
#  ungroup() %>% summarise(t=sum(tot.cost))

```


```{r}
# this is interesting processing of data, but overheads are by expendature type and rules.

# Example: ETD for people cost
#exported %>% filter(str_detect(ExpendOrg,"ETD"), !is.na(Who)) %>% group_by(ItemDate, ExpendType, Who) %>% summarise(tot=sum(BurdenedCost)) #%>% view()
#exported %>% filter(str_detect(ExpendOrg,"ISD"), !is.na(Who)) %>% group_by(ItemDate, ExpendType, Who) %>% summarise(tot=sum(BurdenedCost)) #%>% view()
tmp.sum.who <- exported %>% filter(!is.na(Who)) %>% group_by(org, Who) %>% summarise(tot.burden=sum(BurdenedCost)) #%>% view()

# ETD for overhead cost
#exported %>% filter(str_detect(ExpendOrg,"ETD"), is.na(Who)) %>% group_by(ItemDate) %>% summarise(tot=sum(BurdenedCost)) %>% arrange(ItemDate) #%>% view()
#exported %>% filter(str_detect(ExpendOrg,"ISD"), is.na(Who)) %>% group_by(ItemDate) %>% summarise(tot=sum(BurdenedCost)) %>% arrange(ItemDate) #%>% view()
tmp.sum.oh <- exported %>% filter(is.na(Who)) %>% group_by(org) %>% summarise(tot.burden=sum(BurdenedCost)) #%>% view()

#exported %>% filter(!is.na(Who)) %>% group_by(ItemDate, Who) %>% summarise(tot=sum(BurdenedCost)) %>% arrange(ItemDate) #%>% view()

tmp.who.oh <- tmp.sum.who %>% left_join(tmp.sum.oh, by=join_by(org)) %>% view("who-oh")

#exported %>% filter(str_detect(Who,"ECS")) %>% view()


#examples
# Alyssa
#exported %>% ungroup() %>% filter(ctc=='Q1903.01', str_detect(ExpendOrg,'DO')) %>% arrange(ItemDate) %>% view()
# by task code and full org name
#exported %>% ungroup() %>% group_by(ctc,ExpendOrg) %>% summarise(tot.q=sum(Quantity), tot.b=sum(BurdenedCost)) %>% view()

```


So what do we have after this?   
Hours as claimed per quarter per task. 



```{r}

trans.period <- data.frame(readQ=c("Q1","Q2","Q3"), q=c(1,2,3), y=c(2024, 2024, 2024))

tmp.vars <- bind_rows(list(
  Q1=read_xlsx("../CostVarianceAnalysis/VariancesFY24.xlsx", sheet="FY24Q1"),
  Q2=read_xlsx("../CostVarianceAnalysis/VariancesFY24.xlsx", sheet="FY24Q2"),
  Q3=read_xlsx("../CostVarianceAnalysis/VariancesFY24.xlsx", sheet="FY24Q3")),
  .id="readQ") %>%
  left_join(trans.period, by=join_by(readQ))


tmp.hr.task %>% left_join(tmp.vars, by=join_by(y,q,code)) %>% view()

```


```{r}
p6.by.week.task<- labor$by.week.ctc %>% ungroup() %>% filter(week>=filt.st&week<filt.en) %>%
    select(week, hours=dl.hours, Full.Name=person, task_id, ctc=ctc, role=Role) %>%
    group_by(ctc, Full.Name, task_id, role, week) %>% summarise(tot.hours=sum(hours)) %>% 
    ungroup() %>% 
  
    mutate(LOE=ctc=='Q1903.01')%>%
    mutate(role.new=if_else(LOE=='TRUE'&role!="RA", "LOE", role)) %>%
  mutate(Full.Name=if_else(is.na(Full.Name),role.new,Full.Name)) %>%
  mutate(Last.Name=toupper(str_split_i(Full.Name,", ",i=1))) %>% 
  mutate(q=quarter(week, fiscal_start=10), y=fiscal.year(week), m=fiscal.month(week)) %>%
  select(-Full.Name) %>%
  
  #left_join(select(all$all.data, task_id, ctc, code, name, category, group), by=join_by(task_id)) %>% 
  left_join(select(all$all.data, task_id, code, name, category, group), by=join_by(task_id)) %>% 
  left_join(tmp.vars%>%select(-name), by=join_by(y,q,code)) %>%
  mutate(PercClaim=if_else(is.na(PercClaim),1.0,PercClaim), scaled.tot.hours=tot.hours * PercClaim) %>%
  
    group_by(y,ctc, Last.Name, code,name, role, q) %>% summarise(sum.hours=sum(tot.hours), sum.scaled=sum(scaled.tot.hours))
  
#write_xlsx(p6.by.week.task, "../CostVarianceAnalysis/HoursQuarterPersonTask.xlsx")

p6.by.week.task%>% group_by(y,q) %>% summarise(tot=sum(sum.hours), tot.scaled=sum(sum.scaled))

```



```{r}
tmp.var.mar <- filter(tmp.vars, month=="March")
tmp.var.jun <- filter(tmp.vars,month=="June") 
tmp.var.dec <- filter(tmp.vars,month=="December")

new.cols <- c("month.GEN", "WBS", "activity", "name", "planned%.GEN", "claimed%.GEN", "planned$.GEN", "claimed$.GEN", "variance.GEN", "person.GEN")

names(tmp.var.mar) <- str_replace(new.cols,"GEN","mar")
names(tmp.var.jun) <- str_replace(new.cols,"GEN","jun")
names(tmp.var.dec) <- str_replace(new.cols,"GEN","dec")

tmp.join <- full_join(tmp.var.mar, 
                      tmp.var.jun,
                      by=join_by('WBS', 'activity', "name"), 
                      suffix=c(".mar", ".jun"))

tmp.join <- full_join(tmp.join,
                      tmp.var.dec,  
                      by=join_by('WBS', 'activity', "name"), 
                      suffix=c(".comb", ".dec")
)

tmp.join <- tmp.join %>% 
  mutate(deltaJunMar=variance.jun-variance.mar,
         deltaMarDec=variance.mar-variance.dec,
         diffPerc=`planned%.jun`-`claimed%.jun`) %>%
  arrange(WBS, variance.jun)
```


```{r}

tmp.join.filt <- tmp.join %>% filter(abs(variance.jun)>=0000) %>% select(-contains("%"), -ends_with(".dec"), contains(".jun"),-starts_with("month"), -starts_with("person"))

tmp.join.filt <- left_join(tmp.join.filt, select(all$all.data, activity=code, total_float, baseline_start,target_start, actual_start), 
                           by=join_by(activity)) %>%
  mutate(total_float=total_float/8)

tmp.summ <-tmp.join %>% group_by(WBS) %>% summarise(varJun=sum(variance.jun, na.rm=TRUE),
                                                      varMar=sum(variance.mar, na.rm=TRUE),
                                                      varDec=sum(variance.dec, na.rm=TRUE))

tmp.tots <- tmp.join %>% summarise(varJun=sum(variance.jun, na.rm=TRUE),
                       varMar=sum(variance.mar, na.rm=TRUE),
                       varDec=sum(variance.dec, na.rm=TRUE)
                       ) %>% mutate(deltaJunMar=varJun-varMar,
                                    deltaMarDec=varMar-varDec)

tmp.by.delta <- tmp.join.filt %>% mutate(dir=ifelse(deltaJunMar<0,'l',ifelse(deltaJunMar>0,'g','e'))) %>%
  select(-contains(".mar"), -contains("delta"))


tmp.tots.by.delta <- tmp.by.delta %>% group_by(dir) %>% summarise(t=sum(variance.jun))
# NA = new this quarter



tmp.tots.by.delta

write_xlsx(tmp.by.delta, "variances_by_delta.xlsx")

# all$all.data %>% select(name, code, baseline_start, baseline_end, target_start, target_end, total_float, wbs, status, act_work_qty) %>% view()

```

Extras
the distinct call was added directly to the load all kronos library function.

```{r}
nam="KOWALKOWSKI"
#nam='VALERIO'


charges %>% 
  filter(Last.Name==nam, Timecard.Start>as.Date("2024-10-01"), Timecard.Start<as.Date("2024-12-31")) %>%
  group_by(Timecard.Start, Last.Name) %>% summarise(h=sum(Hours)) %>%
  view("kronos_jbk") # %>% group_by(Last.Name) %>% summarise(tot=sum(h))

exported %>% filter(person==nam) %>% 
  group_by(ItemDate, Who) %>% summarise(h=sum(Quantity)) %>% 
  view("exp_jbk") #%>% group_by(Who) %>% summarise(tot=sum(h))

exported %>% filter(ItemDate==as.Date("2024-10-31")) %>% arrange(ExpendOrg) %>%view()

```

